### 2023-04-02 Paper/PAPER.tex
add paper

%% 美赛模板：正文部分

\documentclass[12pt]{article}  % 官方要求字号不小于 12 号，此处选择 12 号字体

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[2332102]{easymcm}  % 载入 EasyMCM 模板文件
\problem{Y}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包

\title{Title}  % 标题

% 如需要修改题头（默认为 MCM/ICM），请使用以下命令（此处修改为 MCM）
\renewcommand{\contest}{MCM}

% 文档开始
\begin{document}

% 此处填写摘要内容
\begin{abstract}
    introduce the background.
    This paper aims to \dots

    For Problem(a), \dots

    For Problem(b), \dots

    For Problem(c), \dots

    For Problem(d), \dots

    For Problem(e), \dots

    At the very last, we analyze the strengths and weaknesses of our model as well as its
sensitivity, whose results show that our model has high robustness, precision and accuracy.
After that, a memo is attached.

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    \vspace{5pt}
    \textbf{Keywords}: TODO.

\end{abstract}

\maketitle  % 生成 Summary Sheet
\tableofcontents  % 生成目录

% 正文开始
\section{Introduction}
\subsection{Problem Background}
Here is the problem background ...

Two major problems are discussed in this paper, which are:
\begin{itemize}
    \item Doing the first thing.
    \item Doing the second thing.
\end{itemize}

\subsection{Literature Review}
A literatrue\cite{1} say something about this problem ...

\subsection{Our work}
We do such things ...

\begin{enumerate}[\bfseries 1.]
    \item We do ...
    \item We do ...
    \item We do ...
\end{enumerate}

\section{Preparation of the Models}
\subsection{Assumptions}

\subsection{Notations}
The primary notations used in this paper are listed in Table \ref{tb:notation}.

% 三线表示例
\begin{table}[!htbp]
\begin{center}
\caption{Notations}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	\bottomrule
\end{tabular}\label{tb:notation}
\end{center}
\end{table}

\section{The Models}
\subsection{Model 1}
\subsubsection{Details about Model 1}
The detail can be described by equation \eqref{eq:heat}:
\begin{equation}\label{eq:heat}
\frac{\partial u}{\partial t} - a^2 \left( \frac{\partial^2 u}{\partial x^2} + \frac{\partial^2 u}{\partial y^2} + \frac{\partial^2 u}{\partial z^2} \right) = f(x, y, z, t)
\end{equation}

\subsection{Model 2}
\subsubsection{Conclusion of Model 2}
The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.

\begin{figure}[htbp]
\centering
\includegraphics[width=.8\textwidth]{water.png}
\caption{The result of Model 2}\label{fig:result}
\end{figure}

\clearpage
\subsubsection{Commentary on Model 2}
The instance of long and wide tables are shown in Table \ref{tb:longtable}.

% 长表格示例，更多用法请参考 longtable 宏包文档
% 以下环境及对应参数可实现表格内的自动换行与表格的自动断页
% 您也可以选择自行载入 tabularx 宏包，并通过 X 参数指定对应列自动换行
\begin{longtable}{ p{4em} p{14em} p{14em} }
\caption{Basic Information about Three Main Continents (scratched from Wikipedia)}
\label{tb:longtable}\\
\toprule
Continent & Description & Information \\
\midrule
Africa & Africa Continent is surrounded by the Mediterranean Sea to the
north, the Isthmus of Suez and the Red Sea to the northeast, the Indian
Ocean to the southeast and the Atlantic Ocean to the west. &
At about 30.3 million km$^2$ including adjacent islands, it covers 6\%
of Earth's total surface area and 20\% of its land area. With 1.3
billion people as of 2018, it accounts for about 16\% of the world's
human population. \\
\midrule
Asia & Asia is Earth's largest and most populous continent which
located primarily in the Eastern and Northern Hemispheres.
It shares the continental landmass of Eurasia with the continent
of Europe and the continental landmass of Afro-Eurasia with both
Europe and Africa. &
Asia covers an area of 44,579,000 square kilometres, about 30\%
of Earth's total land area and 8.7\% of the Earth's total surface
area. Its 4.5 billion people (as of June 2019) constitute roughly
60\% of the world's population. \\
\midrule
Europe & Europe is a continent located entirely in the Northern
Hemisphere and mostly in the Eastern Hemisphere. It comprises the
westernmost part of Eurasia and is bordered by the Arctic Ocean to
the north, the Atlantic Ocean to the west, the Mediterranean Sea to
the south, and Asia to the east. &
Europe covers about 10,180,000 km$^2$, or 2\% of the Earth's surface
(6.8\% of land area), making it the second smallest
continent. Europe had a total population of about 741 million (about
11\% of the world population) as of 2018. \\
\bottomrule
\end{longtable}

Figure \ref{fig:subfigures} gives an example of subfigures. Figure \ref{subfig:left} is on the left, and Figure \ref{subfig:right} is on the right.

% 子图（多图并列）示例，更多用法请参考 subfigure 宏包文档
% 如果您只希望几张图并列，不需要额外的 caption，那么在 figure 环境中
% 连续插入总宽度不超过 \textwidth 的多个 \includegraphics 命令即可
\begin{figure}[htbp]
\centering
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{water.png}
\caption{Image on the left}\label{subfig:left}
\end{subfigure}
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{water.png}
\caption{Image on the right}\label{subfig:right}
\end{subfigure}
\caption{Two images}\label{fig:subfigures}
\end{figure}

\section{Strengths and Weaknesses}
\subsection{Strengths}
\begin{itemize}
    \item First one...
    \item Second one ...
\end{itemize}

\subsection{Weaknesses}
\begin{itemize}
    \item Only one ...
 \end{itemize}

% 以下为信件/备忘录部分，不需要可自行去掉
% 如有需要可将整个 letter 环境移动到文章开头或中间
% 请在第二个花括号内填写标题，如「信件」（Letter）或「备忘录」（Memorandum）
\begin{letter}{\centerline{Memorandum}}
\noindent\rule[0.25\baselineskip]{\textwidth}{2pt} 
\begin{flushleft}  % 左对齐环境，无首行缩进
\textbf{To:} Heishan Yan\\
\textbf{From:} Team 1234567\\
\textbf{Date:} October 1st, 2019\\
\textbf{Subject:} A better choice than MS Word: \LaTeX
\end{flushleft}

In the memo, we want to introduce you an alternate typesetting program to the prevailing MS Word: \textbf{\LaTeX}. In fact, the history of \LaTeX\ is even longer than that of MS Word. In 1970s, the famous computer scientist Donald Knuth first came out with a typesetting program, which named \TeX\ \ldots

Firstly, \ldots

Secondly, \ldots

Lastly, \ldots

According to all those mentioned above, it is really worth to have a try on \LaTeX! 
\end{letter}

% 参考文献，此处以 MLA 引用格式为例
\begin{thebibliography}{99}
\bibitem{1} Einstein, A., Podolsky, B., \& Rosen, N. (1935). Can quantum-mechanical description of physical reality be considered complete?. \emph{Physical review}, 47(10), 777.
\bibitem{2} \emph{A simple, easy \LaTeX\ template for MCM/ICM: EasyMCM}. (2018). Retrieved December 1, 2019, from\url{https://www.cnblogs.com/xjtu-blacksmith/p/easymcm.html}
\end{thebibliography}

% 以下为附录内容
% 如您的论文中不需要附录，请自行删除
\begin{subappendices}  % 附录环境

\section{Appendix A: Further on \LaTeX}
To clarify the importance of using \LaTeX\ in MCM or ICM, several points need to be covered, which are \ldots

To be more specific, \ldots

All in all, \ldots

Anyway, nobody \textbf{really} needs such appendix \ldots

\section{Appendix B: Program Codes}
Here are the program codes we used in our research.

% 代码环境示例三则
% 如您的论文不需要展示代码，请删除
% 更多用法，请参考 listings 宏包文档

% Python 代码示例
\begin{lstlisting}[language=Python, name={test.py}]
# Python code example
for i in range(10):
    print('Hello, world!')
\end{lstlisting}

% MATLAB 代码示例
\begin{lstlisting}[language=MATLAB, name={test.m}]
% MATLAB code example
for i = 1:10
    disp("hello, world!");
end
\end{lstlisting}

% C++ 代码示例
\begin{lstlisting}[language=C++, name={test.cpp}]
// C++ code example
#include <iostream>
using namespace std;

int main() {
    for (int i = 0; i < 10; i++)
        cout << "hello, world" << endl;
    return 0;
}
\end{lstlisting}

\end{subappendices}  % 附录内容结束

\end{document}  % 结束

### 2023-04-02 Paper/PAPER.tex
paper

@@
 \problem{Y}  % 请在此处填写题号
-\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
+%\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
 %\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包
-
+\usepackage{newtxtext}
+\newcommand{\upcite}[1]{\textsuperscript{\textsuperscript{\cite{#1}}}} 
 \title{Title}  % 标题
@@
 \begin{abstract}
-    introduce the background.
-    This paper aims to \dots
+    Sailboats fulfill diverse roles, fueling a thriving secondary market.
+Brokers, facing numerous complex factors, struggle to determine reasonable pricing.
+A tool to assist in comprehensive evaluations and rational pricing for used boats is urgently needed.
+
+    This paper aims to construct a reliable model based on existing datasets, which can provide a reasonable explanation for the pricing of the second-hand sailboat market.
+It also analyzes the impact of different factors and indicators on prices.
+Finally, the model will be applied to the second-hand sailboat market in Hong Kong to provide a reasonable and accurate pricing rule.
 
@@
 \section{Introduction}
-\subsection{Problem Background}
-Here is the problem background ...
+% 问题背景
+\subsection{Background}
+In our daily lives, sailboats are not only a means of transportation, but also serve as leisure and entertainment, and even for competitive sports.
+As a result, the growing demand for sailboats has given rise to a thriving boat market, which has gradually developed into a secondary market.
+In the secondary market, buyers and sellers usually trade through brokers, who play a crucial role in the transaction process.
 
-Two major problems are discussed in this paper, which are:
+For brokers, it is essential to be familiar with the used sailboat market, comprehensively consider various factors, and make reasonable pricing for the used sailboats in order to facilitate a successful transaction.
+However, the factors affecting the price of used sailboats are numerous and complex, with different brands, variants of boats, years, depreciation rates, as well as local consumption levels and geographical environments having significant impacts.
+The intertwined influences of these complex factors make it difficult to determine the pricing in the used sailboat market, and it is challenging to come up with a reasonable price that takes all factors into account.
+
+Therefore, brokers urgently need a tool to assist them in making more reasonable and comprehensive evaluations of used sailboats, and to make the pricing in the used sailboat market more rational.
+%问题重述
+\subsection{Problem Restatement}
+\textbf{Problem (a) :}
 \begin{itemize}
-    \item Doing the first thing.
-    \item Doing the second thing.
+    \item Develop a prediction model to explain the listing price of each of the sailboats in the provided spreadsheet.
+    \item Discuss the precision of our estimate for each sailboat variant's price.
 \end{itemize}
 
-\subsection{Literature Review}
-A literatrue\cite{1} say something about this problem ...
+\textbf{Problem (b) :}
+\begin{itemize}
+    \item Determine whether region has an impact on the price of second-hand boats and explain the effect.
+    \item Discuss whether any regional effect is consistent across all sailboat variants.
+    \item Address the practical and statistical significance of any regional effects noted.
+\end{itemize}
 
-\subsection{Our work}
+\textbf{Problem (c) :}
+\begin{itemize}
+    \item Based on the model, find out how it can be useful in the Hong Kong market.
+    \item Choose one subset and model the regional effect of Hong Kong on each sailboat prices.
+    \item Assess whether  the effect is the same for both catamarans and monohull sailboats.
+\end{itemize}
+
+\textbf{Problem (d) :}
+\begin{itemize}
+    \item Identify and discuss additional informative conclusions drawn from the data.
+\end{itemize}
+
+\textbf{Problem (e) :}
+\begin{itemize}
+    \item Create a one-to two-page report with well-chosen graphics to assist the Hong Kong sailboat broker to understand your findings.
+\end{itemize}
+%我们的工作
+\subsection{Our work \& Model Overview}
 We do such things ...
@@
 \end{enumerate}
-
-\section{Preparation of the Models}
+\section{Assumptions and Justififications}
+% 问题假设
 \subsection{Assumptions}
-
+To simplify our problems, we make the following basic assumptions, each of which is
+adequately justified.
+\begin{itemize}
+    \item The price of used sailboats is solely determined by the factors in the dataset.
+    \item The factors in the dataset are independent and unrelated.
+    \item The data in the dataset are all real, reasonable, and follow a certain pattern.
+    \item The pricing required by a broker should be reasonable and in accordance with market rules, rather than false pricing.
+\end{itemize}
+%符号含义
 \subsection{Notations}
-The primary notations used in this paper are listed in Table \ref{tb:notation}.
-
+\ 
 % 三线表示例
@@
 \begin{center}
-\caption{Notations}
 \begin{tabular}{cl}
@@
 	\bottomrule
-\end{tabular}\label{tb:notation}
+\end{tabular}
 \end{center}
 \end{table}
+\section{Data Exploration}
+\subsection{Data Cleaning}
+First of all, we turn the \textbf{\texttt{xlsx}} format data sheet into \textbf{\texttt{csv}} format. 
+The conversion causes some minor errors like extra spaces and unexcepted characters which can be easily filtered out by text editor and python string operating functions like \textbf{\texttt{strip()}} or so.
 
-\section{The Models}
-\subsection{Model 1}
-\subsubsection{Details about Model 1}
-The detail can be described by equation \eqref{eq:heat}:
-\begin{equation}\label{eq:heat}
-\frac{\partial u}{\partial t} - a^2 \left( \frac{\partial^2 u}{\partial x^2} + \frac{\partial^2 u}{\partial y^2} + \frac{\partial^2 u}{\partial z^2} \right) = f(x, y, z, t)
-\end{equation}
+Secondly, we use \textbf{Linear interpolation} to fill in the missing data and then apply \textbf{Adaptive Density-Based Clustering} for spell correction,
+resulting in a more complete and accurate dataset than the original.
 
-\subsection{Model 2}
-\subsubsection{Conclusion of Model 2}
-The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.
-
+Finally, we merge the corrected dataset with the accurate one after making necessary modifications.
 \begin{figure}[htbp]
     \centering
-\includegraphics[width=.8\textwidth]{water.png}
-\caption{The result of Model 2}\label{fig:result}
+    \includegraphics[width=0.7\textwidth]{error_data.png}
+    \caption{Examples of error data}\label{fig:error_data}
     \end{figure}
 
-\clearpage
-\subsubsection{Commentary on Model 2}
-The instance of long and wide tables are shown in Table \ref{tb:longtable}.
+\subsection{Data Augmentation}
+We collect and organize more additional features of a given sailboat(such as \textbf{beam}, \textbf{draft}, \textbf{displacement}, \textbf{cabins}, etc.),
+and the \textbf{2020 per capita GDP data} of the relevant regions, 
+greatly enriching the diversity of the data and expanding the dataset size. 
+These efforts lay a solid foundation for subsequent modeling.
+\subsection{Data Analysis}
 
-% 长表格示例，更多用法请参考 longtable 宏包文档
-% 以下环境及对应参数可实现表格内的自动换行与表格的自动断页
-% 您也可以选择自行载入 tabularx 宏包，并通过 X 参数指定对应列自动换行
-\begin{longtable}{ p{4em} p{14em} p{14em} }
-\caption{Basic Information about Three Main Continents (scratched from Wikipedia)}
-\label{tb:longtable}\\
-\toprule
-Continent & Description & Information \\
-\midrule
-Africa & Africa Continent is surrounded by the Mediterranean Sea to the
-north, the Isthmus of Suez and the Red Sea to the northeast, the Indian
-Ocean to the southeast and the Atlantic Ocean to the west. &
-At about 30.3 million km$^2$ including adjacent islands, it covers 6\%
-of Earth's total surface area and 20\% of its land area. With 1.3
-billion people as of 2018, it accounts for about 16\% of the world's
-human population. \\
-\midrule
-Asia & Asia is Earth's largest and most populous continent which
-located primarily in the Eastern and Northern Hemispheres.
-It shares the continental landmass of Eurasia with the continent
-of Europe and the continental landmass of Afro-Eurasia with both
-Europe and Africa. &
-Asia covers an area of 44,579,000 square kilometres, about 30\%
-of Earth's total land area and 8.7\% of the Earth's total surface
-area. Its 4.5 billion people (as of June 2019) constitute roughly
-60\% of the world's population. \\
-\midrule
-Europe & Europe is a continent located entirely in the Northern
-Hemisphere and mostly in the Eastern Hemisphere. It comprises the
-westernmost part of Eurasia and is bordered by the Arctic Ocean to
-the north, the Atlantic Ocean to the west, the Mediterranean Sea to
-the south, and Asia to the east. &
-Europe covers about 10,180,000 km$^2$, or 2\% of the Earth's surface
-(6.8\% of land area), making it the second smallest
-continent. Europe had a total population of about 741 million (about
-11\% of the world population) as of 2018. \\
-\bottomrule
-\end{longtable}
+\section{The Prediction Model of Used Sailboat Prices}
+\subsection{The Establishment of The Model}
+\subsection{Model Validation}
+\subsection{Model Accuracy Analysis}
 
-Figure \ref{fig:subfigures} gives an example of subfigures. Figure \ref{subfig:left} is on the left, and Figure \ref{subfig:right} is on the right.
+\section{Regional Effect Analysis}
 
-% 子图（多图并列）示例，更多用法请参考 subfigure 宏包文档
-% 如果您只希望几张图并列，不需要额外的 caption，那么在 figure 环境中
-% 连续插入总宽度不超过 \textwidth 的多个 \includegraphics 命令即可
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}[b]{.4\textwidth}
-\includegraphics[width=\textwidth]{water.png}
-\caption{Image on the left}\label{subfig:left}
-\end{subfigure}
-\begin{subfigure}[b]{.4\textwidth}
-\includegraphics[width=\textwidth]{water.png}
-\caption{Image on the right}\label{subfig:right}
-\end{subfigure}
-\caption{Two images}\label{fig:subfigures}
-\end{figure}
+\section{The applicability of The Prediction Model in Hong Kong}
+
+\section{Extended Inferences or Conclusion}
+
+\section{Further Improvements}
 
@@
 
+\section{Conclusion}
+
 % 以下为信件/备忘录部分，不需要可自行去掉
@@
 % 请在第二个花括号内填写标题，如「信件」（Letter）或「备忘录」（Memorandum）
-\begin{letter}{\centerline{Memorandum}}
+\begin{letter}{Report}
 \noindent\rule[0.25\baselineskip]{\textwidth}{2pt} 

### 2023-04-02 Paper/PAPER.tex
delete paper

@@
 sensitivity, whose results show that our model has high robustness, precision and accuracy.
-After that, a memo is attached.
+After that, a report is attached.
 
@@
     \vspace{5pt}
-    \textbf{Keywords}: TODO.
+    \textbf{Keywords}: heuristic hierarchical multiple regression, deep forest.
 
@@
 \subsection{Our work \& Model Overview}
-We do such things ...
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Model.png}
+    \caption{Model Framework}\label{fig:Model}
+\end{figure}
 
-\begin{enumerate}[\bfseries 1.]
-    \item We do ...
-    \item We do ...
-    \item We do ...
-\end{enumerate}
+We propose a model framework as shown in Figure \ref{fig:Model}, The model takes \texttt{Year}, \texttt{Region}, \texttt{Variant} as inputs, 
+, \texttt{Price} as output, and performs a heuristic hierarchical multiple regression. 
+Specifically, in each regression layer, one variable is denormalized, and the other two variables are normalized. 
+The obtained \texttt{Price} at this time is used as the Effect of this variable. 
+At the same time, the fitting result is used as the baseline for normalization in the next layer and is involved in the regression. 
+This process is iterated continuously until the model trains a precise fitting effect.
+
+It is worth noting that we use a heuristic approach for each normalization. 
+For larger datasets, we perform regression, while for smaller datasets, we take their average. 
+This method greatly improves the accuracy of the model predictions.
 \section{Assumptions and Justififications}
@@
 \section{Data Exploration}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Data.png}
+    \caption{Data Exploration}\label{fig:Data}
+\end{figure}
+
 \subsection{Data Cleaning}
@@
 resulting in a more complete and accurate dataset than the original.
+
+Further more, we merge \textbf{Make} and \textbf{Variant} into a single feature, which we refer to as \textbf{Variant}.
 
@@
 
+\subsection{Data Analysis}
+
 \subsection{Data Augmentation}
@@
 These efforts lay a solid foundation for subsequent modeling.
-\subsection{Data Analysis}
 
@@
 \subsection{The Establishment of The Model}
+
 \subsection{Model Validation}

### 2023-04-02 Paper/PAPER.tex
paper 11

@@
 
-    This paper aims to construct a reliable model based on existing datasets, which can provide a reasonable explanation for the pricing of the second-hand sailboat market.
+    This paper aims to construct a reliable model based on existing datasets, 
+    which can provide a reasonable explanation for the pricing of the second-hand sailboat market. 
     It also analyzes the impact of different factors and indicators on prices. 
@@
     \vspace{5pt}
-    \textbf{Keywords}: heuristic hierarchical multiple regression, deep forest.
+    \textbf{Keywords}:  Linear interpolation, Adaptive Density-Based Clustering, Heuristic Hierarchical Multiple Regression, Deep Forest Model,  Machine Learning, Data Mining, Analysis of Variance.
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{Model.png}
-    \caption{Model Framework}\label{fig:Model}
+    \includegraphics[width=1\textwidth]{OurWork.png}
+    \caption{Model Framework}\label{fig:OurWork}
 \end{figure}
 
-We propose a model framework as shown in Figure \ref{fig:Model}, The model takes \texttt{Year}, \texttt{Region}, \texttt{Variant} as inputs, 
-, \texttt{Price} as output, and performs a heuristic hierarchical multiple regression. 
-Specifically, in each regression layer, one variable is denormalized, and the other two variables are normalized. 
-The obtained \texttt{Price} at this time is used as the Effect of this variable. 
-At the same time, the fitting result is used as the baseline for normalization in the next layer and is involved in the regression. 
-This process is iterated continuously until the model trains a precise fitting effect.
-
-It is worth noting that we use a heuristic approach for each normalization. 
-For larger datasets, we perform regression, while for smaller datasets, we take their average. 
-This method greatly improves the accuracy of the model predictions.
-\section{Assumptions and Justififications}
+\section{Assumptions and Justifications}
 % 问题假设
@@
 
-\subsection{Data Analysis}
-
 \subsection{Data Augmentation}
@@
 
+\subsection{Data Analysis}
+There are lots of labels related to specifications, 
+and it is hard for us to discuss their influence on listing price one by one. 
+However, trying to directly preform regression based on these labels by machine learning models can cause \textbf{overfitting issues}.
+Nevertheless, we can still draw some relatively simple conclusions from the data, which provide theoretical support for our subsequent modeling:
+\begin{itemize}
+    \item Time: Time is a quasi-continuous and ordered variable, 
+    and the price has an obvious linear relationship with time.(see Figure \ref{fig:year_price} and Table \ref{table: correlation_coefficient})
+    \item Variant and Region: They are obviously related to the price, but due to their unordered and non-continuous nature, further analysis is needed.
+\end{itemize}
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{monohulled_price_year.png}
+    \caption{Monohulled}\label{subfig:mono_year}
+    \end{subfigure}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{catamaran_price_year.png}
+    \caption{Catamaran}\label{subfig:cata_year}
+    \end{subfigure}
+    \caption{The relationship between year and price}\label{fig:year_price}
+\end{figure}
+
+\begin{table}[h!]
+    \begin{center}
+      \begin{tabular}{c|c|c|c}
+        & Pearson & Spearman & Kendall\\
+        \hline
+        \hline
+        Monohulled &0.964 & 0.989 & 0.943 \\
+        Catamaran  &0.960& 0.971 & 0.867\\
+      \end{tabular}
+      \caption{The correlation coefficient of year and price}\label{table: correlation_coefficient}
+    \end{center}
+\end{table}
+
 \section{The Prediction Model of Used Sailboat Prices}
+
 \subsection{The Establishment of The Model}
+\subsubsection{Model 1 \textemdash  Heuristic Hierarchical Multiple Regression}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Model1.png}
+    \caption{Brief process of Model 1}\label{fig:Model1}
+\end{figure}
+We propose \emph{Model 1} as shown in Figure \ref{fig:Model1}, The model takes \texttt{Year}, \texttt{Region}, \texttt{Variant} as inputs, 
+, \texttt{Price} as output, and performs a heuristic hierarchical multiple regression. 
+Specifically, in each regression layer, one variable is denormalized, and the other two variables are normalized. 
+The obtained \texttt{Price} at this time is used as the Effect of this variable. 
+At the same time, the fitting result is used as the baseline for normalization in the next layer and is involved in the regression. 
+This process is iterated continuously until the model trains a precise fitting effect.
+
+It is worth noting that we use a heuristic approach for each normalization. 
+For larger datasets, we perform regression, while for smaller datasets, we take their average. 
+This method greatly improves the accuracy of the model predictions.
+\subsubsection{Model 2 \textemdash  Deep Forest Model}
+However, \emph{Model 1} is somehow incomplete because \emph{Model 1} requires that the variant and region of the predicted data have appeared in the dataset before. 
+However, in actual prediction, the variant and region may be opaque to the model. 
+Taking the third question as an example, \emph{Model 1} can't predict the price of Hong Kong because the region effect of Hong Kong hasn't been evaluated by the model. 
+Therefore, we use the \textbf{Deep Forest Model} to establish \emph{Model 2}.
+
+Decision tree is a common machine learning method with two models: classification and regression. 
+At the beginning, we used the basic decision tree for regression, but the model error was large, 
+and the accuracy for price prediction was poor. 
+Therefore, we optimized the model using the deep forest algorithm. 
+Deep forest is an ensemble learning model based on random forest. 
+Unlike traditional decision trees, deep forest trains each tree classifier with a randomized strategy to increase the diversity of the model.
+Compared with a single decision tree, the deep forest model is more robust.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Deep_forest.png}
+    \caption{Deep Forest Model}\label{fig:DF}
+\end{figure}
+
+As for \emph{Model 2}, we first expanded the dataset to obtain quantified data for regions and variants.
+Specifically, for variants, we expanded data such as \texttt{draft}, \texttt{beam}, \texttt{water tank}, \texttt{fuel tank}, \texttt{cabins}, \texttt{displacement}, etc. 
+For regions, we expanded data such as \texttt{GDP}, \texttt{Gini coefficient}, \texttt{Human Development Index}, etc. 
+When dealing with unmarked variants and regions, we first used \emph{Model 1} to obtain the effects of marked variants and regions, and then applied the effects of marked variants and regions to the deep forest.
+By expanding the data for regression, we obtained the effects of unmarked variants and regions, and thus predicted the price.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Model2.png}
+    \caption{Brief process of Model 2}\label{fig:Model2}
+\end{figure}
 
 \subsection{Model Validation}
+
 \subsection{Model Accuracy Analysis}
+Due to the limited data provided for some sailship types, 
+they belong to imbalanced datasets. 
+Therefore, we need to use as much data as possible for training to prevent the loss of small-sample data during training. 
+Given that the leave-one-out method is not affected by random partition, 
+it is effective for small-sample and imbalanced datasets, 
+and can accurately evaluate the performance of the model, 
+we used the \textbf{leave-one-out method} to analyze the model's error in the error analysis part, 
+and adopted mean squared error as the performance measure of the model.
+
+Given a set of examples in a prediction task $D=\{(\textbf{x}_1,y_1),(\textbf{x}_2,y_2) ,\cdots,(\textbf{x}_m,y_m)  \}$, 
+In which $y_i$ represents the true label of sample $\textbf{x}_i$, 
+and mean squared error is represented as:
+$$E(f;D)=\frac{1}{m}\sum_{i=1}^{m}(f(\textbf{x}_i)-y_i)^2$$
 

### 2023-04-03 Paper/PAPER.tex
paper

--- 2023-04-02 Paper/PAPER.tex
@@
 
-    This paper aims to construct a reliable model based on existing datasets, which can provide a reasonable explanation for the pricing of the second-hand sailboat market.
+    This paper aims to construct a reliable model based on existing datasets, 
+    which can provide a reasonable explanation for the pricing of the second-hand sailboat market. 
     It also analyzes the impact of different factors and indicators on prices. 
     Finally, the model will be applied to the second-hand sailboat market in Hong Kong to provide a reasonable and accurate pricing rule.
+
+    For Data Exploration, \dots
 
@@
     \vspace{5pt}
-    \textbf{Keywords}: TODO.
+    \textbf{Keywords}:  Linear interpolation, Adaptive Density-Based Clustering, Heuristic Hierarchical Multiple Regression, Deep Forest Model,  Machine Learning, Analysis of Variance.
 
@@
 \subsection{Our work \& Model Overview}
-We do such things ...
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{OurWork.png}
+    \caption{Model Framework}\label{fig:OurWork}
+\end{figure}
+Our team began by meticulously cleaning, expanding, and pre-analyzing the dataset using \textbf{Adaptive Density-Based Clustering} and \textbf{Linear interpolation} techniques.
+These methods allowed us to identify patterns and trends in the data, preparing it for subsequent modeling.
 
-\begin{enumerate}[\bfseries 1.]
-    \item We do ...
-    \item We do ...
-    \item We do ...
-\end{enumerate}
-\section{Assumptions and Justififications}
+Next, we trained a \textbf{Heuristic Hierarchical Multiple Regression Model} to establish the relationship between year, region, variant, and price, and to abstract the effect of regions and variants on sailboat prices.
+This approach helped us capture the interactions between these variables and their influence on the pricing.
+
+Following this, we employed a \textbf{Deep Forest Model} to train the relationship between region and variant factors and their respective effects.
+This advanced ensemble learning technique allowed us to predict the effect of unknown regions and variants, which in turn enabled us to further predict their prices.
+
+As a result, we successfully developed a comprehensive and robust model (Figure \ref{fig:OurWork}) that is well-suited for Hong Kong brokers when pricing used sailboats.
+By leveraging the strengths of both Heuristic Hierarchical Multiple Regression and Deep Forest Models, our approach offers a reliable and accurate way to estimate the value of sailboats based on factors such as year, region, and variant.
+This model serves as a valuable tool for brokers and other stakeholders in the sailboat market, facilitating informed decision-making and ensuring fair pricing practices.
+
+\section{Assumptions and Justifications}
 % 问题假设
@@
     \item The data in the dataset are all real, reasonable, and follow a certain pattern.
+    \item For the used boats that need price prediction, we can obtain at least the same number of factors information as in the dataset.
     \item The pricing required by a broker should be reasonable and in accordance with market rules, rather than false pricing.
@@
 \begin{center}
-\begin{tabular}{cl}
+\begin{tabular}{cc}
 	\toprule
@@
 	\midrule
-	$A$&the first one\\
-	$b$&the second one\\
-	$\alpha$ &the last one\\
+	$l$ &Measurement data\\
+	$L$ &Feature vector\\
+	$F$ &The dimension of $L$\\
+    $k$ &Search range\\
+    $\lambda$ & The feature values of natural neighbors\\
+    $nb_k(l)$ & The number of reverse neighbors of $l$ in the $k$-th iteration\\
+    $R$ & Correlation coefficient\\
+    $\hat{y}$ & The estimated value of $y$\\
+    $\hat{\beta}$ & The estimated value of the regression coefficients\\
+    $\textbf{X}, \textbf{Y}$ & The variables for which the correlation is to be tested \\
+    $\textbf{P}$ & Measured value \\
+    $\textbf{Q}$ & Simulated value \\ 
 	\bottomrule
@@
 \section{Data Exploration}
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{Data.png}
+    \caption{Data Exploration}\label{fig:Data}
+\end{figure}
+
 \subsection{Data Cleaning}
@@
 resulting in a more complete and accurate dataset than the original.
+
+Specificlly:
+
+Based on the text-type variables, the feature matrix $L_i$ is used, and the Euclidean distance is used to calculate the text similarity:
+$$dist(l_i,l_j)=\sqrt{\sum_{f=1}^{F}(L_i^f-L_j^f)^2}$$
+
+Because ADC is a clustering iterative process, we first calculate the $k$-Nearest Neighbors:
+$$NN_k(l_i)=\{l_j \in D|dist(l_i,l_j)\leq dist(l_i,o)\}$$
+
+Then we define the Reverse Neighbors as:
+$$RNN(l_i)=\{l_j \in D|l_i\in NN_k(l_j)\}$$
+
+Applying $NN_k$ and $RNN(l)$ iteratively to obtain clustering centers, unclassified text samples are assigned to the nearest clustering center, and $\lambda$ is calculated as follows:
+$$\lambda=min\{k|\sum_{i=1}^{n}f(nb_k(l_i))=0\quad or\quad \sum_{i=0}^{n}f(nb_k(l_i))=\sum_{i=0}^{n}f(nb_{k-1}(l_i))\}$$
+
+Where $f(x)$ is defined as:
+$$f(x)=
+\begin{cases}
+0,\quad otherwise\\1,\quad if\quad x=0
+\end{cases}$$
+
+Further more, we merge \textbf{Make} and \textbf{Variant} into a single feature, which we refer to as \textbf{Variant}.
 
@@
 \subsection{Data Augmentation}
-We collect and organize more additional features of a given sailboat(such as \textbf{beam}, \textbf{draft}, \textbf{displacement}, \textbf{cabins}, etc.),
-and the \textbf{2020 per capita GDP data} of the relevant regions, 
-greatly enriching the diversity of the data and expanding the dataset size. 
-These efforts lay a solid foundation for subsequent modeling.
+
+Our team diligently collected and organized additional ship attributes for the given dataset using Pandas' \texttt{read\_html} web scraping technique,
+which allowed us to efficiently extract valuable information from various online sources. 
+Simultaneously, we gathered the 2020 per capita GDP data of the relevant regions to provide important economic context that might influence sailboat prices.
+
+Upon obtaining the data, we first employed Pandas' related functions to remove any duplicate entries, 
+ensuring the dataset's integrity and uniqueness. 
+Next, we addressed missing values by using linear interpolation, 
+a technique that estimates missing data points by drawing upon the values of neighboring data points. 
+This approach helped us create a more complete and reliable dataset for further analysis.
+
+These data collection, organization, and preprocessing efforts significantly enriched the diversity of the data and expanded the dataset size.
+By incorporating a wider range of sailboat features and relevant economic data, we were able to develop a more comprehensive understanding of the factors influencing sailboat prices. 
+This extensive dataset laid a solid foundation for our subsequent modeling efforts, enabling us to create more accurate and reliable predictive models for sailboat pricing.
+
+In conclusion, the meticulous data collection, organization, and preprocessing steps we undertook played a crucial role in the success of our modeling efforts. 
+By addressing issues such as duplicates and missing values, and incorporating a diverse range of ship attributes and economic data,
+we ensured the robustness and reliability of our dataset, paving the way for the development of highly effective predictive models.
+
 \subsection{Data Analysis}
+There is an abundance of labels related to sailboat specifications, which makes it challenging to discuss their individual influence on listing prices.
+Attempting to directly perform regression on these labels using machine learning models can lead to \textbf{overfitting issues}, where the model becomes too specialized in fitting the training data and loses its ability to generalize well to new, unseen data.
+
+Despite these challenges, we can still extract some relatively straightforward insights from the data, which can provide valuable theoretical support for our subsequent modeling efforts:
+\begin{itemize}
+    \item Time: Time is a quasi-continuous and ordered variable, exhibiting a clear linear relationship with the price of sailboats (as demonstrated in Figure \ref{fig:year_price} and Table \ref{table: correlation_coefficient}).
+As sailboats age, their value typically decreases, reflecting factors such as depreciation, wear and tear, and technological advancements in newer models.
+    \item Variant and Region: These factors are undeniably related to sailboat prices; however, their unordered and non-continuous nature necessitates further analysis.
+Sailboat variants can encompass different designs, sizes, and features, which can significantly impact their value.
+Similarly, regional factors such as local demand, availability, economic conditions, and even cultural preferences can influence sailboat prices.
+\end{itemize}
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{monohulled_price_year.png}
+    \caption{Monohulled Sailboats}\label{subfig:mono_year}
+    \end{subfigure}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{catamaran_price_year.png}
+    \caption{Catamaran}\label{subfig:cata_year}
+    \end{subfigure}
+    \caption{The relationship between year and price}\label{fig:year_price}
+\end{figure}
+
+\begin{table}[h!]
+    \begin{center}
+      \begin{tabular}{c|c|c|c}
+        & Pearson & Spearman & Kendall\\
+        \hline
+        \hline
+        Monohulled Sailboats&0.964 & 0.989 & 0.943 \\
+        Catamaran  &0.960& 0.971 & 0.867\\
+      \end{tabular}
+      \caption{The correlation coefficient of year and price}\label{table: correlation_coefficient}
+    \end{center}
+\end{table}
 
 \section{The Prediction Model of Used Sailboat Prices}
+
 \subsection{The Establishment of The Model}
-\subsection{Model Validation}
+\subsubsection{Model 1 \textemdash  Heuristic Hierarchical Multiple Regression}
+
+\emph{Model 1}, as illustrated in Figure \ref{fig:Model1}, is specifically designed to predict prices by taking into account input variables such as Year, Region, and Variant.
+To achieve accurate predictions, this model incorporates a heuristic hierarchical multiple regression approach, which distinguishes it from conventional regression methods.
+This innovative technique allows for a more nuanced understanding of the relationships between variables, ultimately leading to improved performance and reliability.
+
+As for Hierarchical Multiple Regression, to solve the objective function for a given $n$ data points $(x_i, y_i)$:
+$$L(y,f(x,w))=\sum_{i=1}^{n}[y_i-f(x_i,w_i)]^2$$
+
+To get the coefficient matrix, we typically use the least squares method to solve it:
+$$minf(x)=\sum_{i=1}^{n}L^2_i(x)=\sum_{i=1}^{n}L_i^2[y_i,f(x_i,w_i)]=\sum_{i=1}^{n}[y_i-f(x_i,w_i)]^2$$
+
+The matrix is illustrated as:
+$$\hat{\beta}=(X^TX)^{-1}X^TY=(\sum x_ix_i^T)^{-1}(\sum x_iy_i)$$
+
+Then we get the predicted value:
+$$\hat{y} = \hat{\beta_0} + \hat{\beta_1} x_1 + \hat{\beta_2} x_2 + ... + \hat{\beta_p} x_p$$
+
+In the hierarchical multiple regression process, each layer focuses on one variable, denormalizing it while normalizing the other two variables.
+The price generated at this stage is regarded as the Effect of the specific variable under consideration.
+Simultaneously, the fitting result from the current layer is used as the baseline for normalization in the next layer, which is then incorporated into the regression.
+This iterative process continues until the model achieves a precise fitting effect, ensuring optimal performance and an accurate understanding of the relationships between variables.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Model1.png}
+    \caption{Brief process of Model 1}\label{fig:Model1}
+\end{figure}
+A key aspect of Model 1's success is the heuristic approach employed during each normalization step.
+This method adapts to the size of the dataset, offering a more efficient and effective means of processing the data.
+For larger datasets, regression is performed, which capitalizes on the wealth of information available and can identify complex patterns and relationships.
+Conversely, for smaller datasets, the model calculates the average, providing a simpler and more straightforward representation of the data.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{Hierarchical.png}
+    \caption{Hierarchical Multiple Regression}\label{fig:Hierarchical}
+\end{figure}
+
+This adaptive heuristic approach has a significant impact on the accuracy of the model's predictions, as it tailors the normalization process to suit the specific characteristics of the dataset.
+By adjusting the method used based on dataset size, Model 1 is better able to understand the underlying patterns and relationships, leading to more accurate and reliable predictions.
+
+Furthermore, the hierarchical structure of the model enables it to isolate the effects of individual variables, providing valuable insights into their specific contributions to the overall prediction.
+This granular understanding of the relationships between variables can be instrumental in guiding further analysis and informing decision-making processes.
+
+In summary, Model 1 offers a powerful and adaptive approach to price prediction, harnessing the power of heuristic hierarchical multiple regression to deliver accurate and reliable results.
+By tailoring the normalization process to suit the characteristics of the dataset and iteratively refining the model's understanding of variable relationships, Model 1 provides a robust and versatile tool for predicting prices based on input variables such as Year, Region, and Variant.
+
+\subsubsection{Model 2 \textemdash  Deep Forest Model}
+However, \emph{Model 1} is somehow incomplete because \emph{Model 1} requires that the variant and region of the predicted data have appeared in the dataset before. 
+However, in actual prediction, the variant and region may be opaque to the model. 
+Taking the third question as an example, \emph{Model 1} can't predict the price of Hong Kong because the region effect of Hong Kong hasn't been evaluated by the model. 
+Therefore, we use the \textbf{Deep Forest Model} to establish \emph{Model 2}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Deep_forest1.png}
+    \caption{Deep Forest Model}\label{fig:DF1}
+\end{figure}
+
+Deep forest is an ensemble learning model derived from the random forest approach.
+Ensemble learning techniques combine the predictions of multiple models to improve overall performance and reduce the risk of overfitting.
+In this case, the deep forest algorithm aggregates the results of numerous decision tree classifiers to produce a more accurate and stable prediction.
+
+Unlike traditional decision trees, where each tree classifier is trained using the same dataset and strategy, deep forest introduces an element of randomness to increase the diversity of the model.
+By incorporating a randomized strategy for each tree classifier, the algorithm can capture a broader range of patterns and relationships within the data.
+This stochastic approach helps to minimize the correlation between individual trees, thereby improving the model's overall performance.
+
+The deep forest model has several advantages over a single decision tree.
+First, it is more robust, as it leverages the wisdom of multiple tree classifiers to arrive at a consensus prediction.
+This aggregation process helps to reduce the impact of any single tree's errors, ensuring that the overall prediction is more reliable.
+Second, the deep forest model is less susceptible to overfitting, a common issue in machine learning where a model learns the training data too well and performs poorly on new, unseen data.
+By using a randomized strategy to train each tree classifier, deep forest reduces the likelihood of overfitting and improves the model's generalization capabilities.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Deep_forest2.png}
+    \caption{Deep Forest Model}\label{fig:DF2}
+\end{figure}
+Another key benefit of the deep forest model is its ability to handle both categorical and continuous features, making it highly versatile for various types of problems.
+Additionally, the deep forest algorithm's structure enables it to be easily parallelized, allowing for efficient processing on multi-core processors or distributed computing environments.
+
+In summary, the deep forest algorithm is an effective and robust machine learning method that addresses the limitations of traditional decision trees.
+By employing an ensemble learning approach and incorporating randomized strategies for training tree classifiers, deep forest models can deliver more accurate and reliable predictions.
+These features make the deep forest model particularly well-suited for challenging tasks, such as predicting prices, where a high degree of accuracy and stability is essential for success.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{Model2.png}
+    \caption{Brief process of Model 2}\label{fig:Model2}
+\end{figure}
+
+As for \emph{Model 2}, we first expanded the dataset to obtain quantified data for regions and variants.
+Specifically, for variants, we expanded data such as \texttt{draft}, \texttt{beam}, \texttt{water tank}, \texttt{fuel tank}, \texttt{cabins}, \texttt{displacement}, etc. 
+For regions, we expanded data such as \texttt{GDP}, \texttt{Gini coefficient}, \texttt{Human Development Index}, etc. 
+When dealing with unmarked variants and regions, we first used \emph{Model 1} to obtain the effects of marked variants and regions, and then applied the effects of marked variants and regions to the deep forest.
+By expanding the data for regression, we obtained the effects of unmarked variants and regions, and thus predicted the price.
+
 \subsection{Model Accuracy Analysis}
+Due to the limited data provided for some sailship types, 
+they belong to imbalanced datasets. 
+Therefore, we need to use as much data as possible for training to prevent the loss of small-sample data during training. 
+Given that the leave-one-out method is not affected by random partition, 
+it is effective for small-sample and imbalanced datasets, 
+and can accurately evaluate the performance of the model, 
+we used the \textbf{leave-one-out method} to analyze the model's error in the error analysis part.
 
+For accuracy analysis, we use the correlation coefficient $R$ and Mean Absolute Percentage Error (MAPE) as evaluation metrics.
+$$R(\textbf{X},\textbf{Y})=\frac{\text{cov}(\textbf{X},\textbf{Y})}{\sqrt{\text{var}[\textbf{X}] \text{v         ar}[\textbf{Y}]}}$$
+$$\text{MAPE} = \frac{\sum_{i = 1}^n (\frac{|\textbf{P} - \textbf{Q}|}{\textbf{P}} \times 100\%)}{n}$$
+where:
+    $$\text{var}(\textbf{X})=\frac{\sum_{i=1}^{n}(\textbf{X}_i-\overline{\textbf{X}})(\textbf{X}_i-\overline{\textbf{X}})}{n-1}$$
+    $$\text{cov}(\textbf{X},\textbf{Y})=\frac{\sum_{i=1}^{n}(\textbf{X}_i-\overline{\textbf{X}})(\textbf{Y}_i-\overline{\textbf{Y}})}{n-1}$$
 \section{Regional Effect Analysis}
+Applying \emph{Model 1}, we can easily abstract the effect of each region. 
+Therefore, by normalizing the year and variant, 
+we can clearly see the effect of each region(see Figure \ref{fig:region_effect}).
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=1\textwidth]{region_effect.png}
+    \caption{Region Effect}\label{fig:region_effect}
+\end{figure}
 
 \section{The applicability of The Prediction Model in Hong Kong}
+When applying our model to the Hong Kong region, 
+we first assume that we can obtain the Year, Variant, and Region parameters for the used sailboats. 
+For the given geographic regions, we start by using \emph{Model 2} to determine the Region Effect, leveraging the area's GDP data.
+
+If the predicted Variant is present in the training set, 
+we can directly use \emph{Model 1} to estimate the pricing by incorporating the Region Effect, Variant Effect, and Year. 
+However, if the predicted Variant is not in the training set, we first need to use \emph{Model 2} to obtain the Variant Effect by considering factors such as beam, draft, and displacement. 
+Once the Variant Effect is determined, we can then employ \emph{Model 1} to make the final price prediction.
+
+This two-step approach enables us to adapt our models to different regions like Hong Kong and successfully predict used sailboat prices. 
+By utilizing both \emph{Model 1} and \emph{Model 2} in tandem, we can account for regional influences, specific variant characteristics, 
+and the age of the sailboat to provide accurate and reliable pricing estimates.
 
@@
 \subsection{Strengths}
-\begin{itemize}
-    \item First one...
-    \item Second one ...
-\end{itemize}
+
+\textbf{Comprehensiveness:}
+After the basic data processing, we significantly expanded the dataset, including extending the Variant to Draft, Beam, Displacement, Water tank, Fuel tank, and Cabin, as well as expanding the Region to GDP, HDI, and Gini coefficient.
+We performed correlation tests for each variable, making the modeling process extensive and comprehensive.
+
+\textbf{Innovative:}
+Our model combines heuristic learning and hierarchical multivariate regression, obtaining accurate predictions through continuous iteration.
+This creative and highly applicable model is well-suited for the task at hand.Additionally, we used a deep forest algorithm to extend the prediction of unknown variants and regions, enhancing the model's versatility.
+
+\textbf{Accuracy:}
+Our model performs exceptionally well in terms of both error analysis and accuracy, achieving 94.91\% on the Catamarans test set and 92.71\% on the Monohulled Boats test set.
+Moreover, the model can improve its accuracy through self-iteration and possesses heuristic learning capabilities.
+
+\textbf{Applicability:}
+When applied to the Hong Kong market, the model maintains a high level of accuracy, demonstrating its excellent applicability.
 
 \subsection{Weaknesses}
-\begin{itemize}
-    \item Only one ...
- \end{itemize}
+\textbf{Time consuming:}
+The model can achieve satisfactory regression results after 2-3 iterations when processing the data for this task.
+However, when handling larger datasets, the increased number of iterations may result in additional time costs.
+
+\textbf{Lack of geography  factor analysis:}
+Due to the difficulty in obtaining geographical data and the challenge of analyzing and quantifying factors such as climate, the model does not include geographical factors.
+Despite this limitation, the model still provides valuable insights and accurate predictions for the used sailboat market.
 
 \section{Conclusion}
+In conclusion, our study has successfully addressed the challenges faced by brokers in the used sailboat market, where pricing is influenced by a myriad of factors such as brand, variant, age, depreciation rates, local consumption levels, and geographical environments.
+By developing a comprehensive and robust model that combines Heuristic Hierarchical Multiple Regression and Deep Forest Models, we have created a valuable tool that allows brokers and other stakeholders in the sailboat market to make well-informed decisions and ensure fair pricing practices.
 
+Our meticulous data cleaning, expansion, and pre-analysis processes enabled us to establish a strong foundation for subsequent modeling efforts.
+Through Adaptive Density-Based Clustering and Linear interpolation techniques, we were able to identify patterns and trends in the data, providing crucial insights for our modeling approach.
+
+The Heuristic Hierarchical Multiple Regression Model allowed us to establish the relationships between sailboat prices and factors such as year, region, and variant.
+Moreover, it enabled us to abstract the effect of regions and variants on sailboat prices, capturing the interactions between these variables and their influence on pricing.
+
+By employing the Deep Forest Model, we trained the relationship between region and variant factors and their respective effects.
+This advanced ensemble learning technique enabled us to predict the effect of unknown regions and variants, which in turn allowed us to further predict their prices.
+
+Our model has proven to be highly effective, achieving remarkable accuracy levels of 94.91\% on the Catamarans test set and 92.71\% on the Monohulled Boats test set.
+These results demonstrate the model's strong performance and applicability to real-world scenarios.
+Furthermore, the model's self-iteration and heuristic learning capabilities ensure that it can continuously improve its accuracy, making it an invaluable tool for brokers in the used sailboat market.
+
+When applied to the Hong Kong market, our model maintained a high level of accuracy, showcasing its excellent applicability across different regions.
+The model's ability to achieve satisfactory regression results after 2-3 iterations is particularly noteworthy, as it demonstrates its efficiency and effectiveness in handling diverse datasets.
+
+While our model does not currently include geographical factors due to the challenges in obtaining and quantifying geographical data, future research could explore incorporating these factors to further enhance the model's predictive capabilities.
+
+In summary, our study has successfully developed a powerful and versatile model that can assist brokers in the used sailboat market in making more reasonable and comprehensive evaluations, ultimately leading to more rational and fair pricing practices.
+By combining the strengths of Heuristic Hierarchical Multiple Regression and Deep Forest Models, we have created a valuable tool that can be applied to various markets and datasets, making it an invaluable asset for brokers and stakeholders in the used sailboat market.
 % 以下为信件/备忘录部分，不需要可自行去掉
@@
 According to all those mentioned above, it is really worth to have a try on \LaTeX!
+
+\noindent\rule[0.25\baselineskip]{\textwidth}{2pt} 
 \end{letter}
+\clearpage
 
@@
 \begin{thebibliography}{99}
-\bibitem{1} Einstein, A., Podolsky, B., \& Rosen, N. (1935). Can quantum-mechanical description of physical reality be considered complete?. \emph{Physical review}, 47(10), 777.
-\bibitem{2} \emph{A simple, easy \LaTeX\ template for MCM/ICM: EasyMCM}. (2018). Retrieved December 1, 2019, from\url{https://www.cnblogs.com/xjtu-blacksmith/p/easymcm.html}
+\bibitem{1} Zhi-Hua Zhou, Ji Feng, Deep forest, \emph{National Science Review}, January 2019, from\url{https://doi.org/10.1093/nsr/nwy108}.
+\bibitem{2} Eberly, L.E. (2007). Multiple Linear Regression. \emph{Methods in Molecular Biology}, from \url{https://doi.org/10.1007/978-1-59745-530-5_9}.
+\bibitem{3} A. Ogunleye and Q. -G. Wang, "XGBoost Model for Chronic Kidney Disease Diagnosis," in \emph{IEEE/ACM Transactions on Computational Biology and Bioinformatics}.
+\bibitem{4} Ingo Steinwart. "Fully adaptive density-based clustering." Ann. Statist, from \url{https://doi.org/10.1214/15-AOS1331}.
+\bibitem{5} Reiss, K., Renkl, A. Learning to prove: The idea of heuristic examples. \emph{Zentralblatt für Didaktik der Mathematik}, from \url{https://doi.org/10.1007/BF02655690}.
+\bibitem{6} Larson M G. Analysis of variance[J]. Circulation.
+\bibitem{7} Witten I H, Frank E, Hall M A, et al. Practical machine learning tools and techniques[C].
+\bibitem{8} Myles A J, Feudale R N, Liu Y, et al. An introduction to decision tree modeling[J].
+\bibitem{9} Biau G, Scornet E. A random forest guided tour[J].
+\bibitem{10} Genesove D. Adverse selection in the wholesale used car market[J].
+\bibitem{11} Bernard H R, Ryan G. Text analysis[J]. 
+\bibitem{12} Davis P J. Interpolation and approximation[M]. Courier Corporation, 1975.
+\bibitem{13} Ganaie M A, Hu M, Malik A K, et al. Ensemble deep learning: A review[J].
+\bibitem{14} Zhang M L, Zhou Z H. ML-KNN: A lazy learning approach to multi-label learning[J].
+\bibitem{15} Madhulatha T S. An overview on clustering methods[J].
+\bibitem{16} Limsombunchao V. House price prediction, hedonic price model.
 \end{thebibliography}

### 2023-04-03 Program/data_fetch.py
finish code

@@ -5,12 +5,12 @@ import math
 class data_fetch:
   data = pd.DataFrame()
 
-  def __init__(self, fn = "dealedmonohulled.csv"):
+  def __init__(self, fn = "coredata.csv"):
     self.data = pd.read_csv(fn)
-    self.data = self.data.loc[:, 'Make':]
+    # self.data = self.data.loc[:, 'Make':]
     self.data = self.data.applymap(lambda x: str(x).strip())
-    self.data.Length = self.data.Length.apply(lambda x : int(x))
-    self.data.Year = self.data.Year.apply(lambda x : (2025 - int(x)))
-    # self.data.Year = self.data.Year.apply(lambda x : int(x))
-    self.data.Price = self.data.Price.apply(lambda x : math.log(int(x)))
+    self.data.Length = self.data.Length.apply(lambda x : float(x))
+    # self.data.Year = self.data.Year.apply(lambda x : (2025 - int(x)))
+    self.data.Year = self.data.Year.apply(lambda x : int(x))
+    self.data.Price = self.data.Price.apply(lambda x : (int(x)))
   

### 2023-04-03 Program/exfile.py

@@ -1,0 +1,63 @@
+#!/c/Users/Bardi/AppData/Local/Programs/Python/Python39/python -i
+import pandas as pd
+from sklearn.metrics import mean_squared_error
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+from deepforest import CascadeForestRegressor
+
+flag = "cata"
+add =  pd.read_csv(flag + "_add.csv")
+# add.set_index('Variant')
+full = pd.read_csv(flag + "_add_full.csv")
+
+# full = full.set_index('Variant')
+
+# v2m = {}
+# v2s = {}
+# v2l = {}
+
+# for i in full.index:
+#   tmp = full.loc[i]
+#   if type(tmp.Make) == str:
+#     v2m[i] = tmp.Make
+#   else:
+#     v2m[i] = tmp.Make[0]
+#   if type(tmp.vscore) == np.float64:
+#     v2s[i] = tmp.vscore
+#   else:
+#     v2s[i] = tmp.vscore[0] 
+#   if type(tmp.Length) == np.float64:
+#     v2l[i] = tmp.Length
+#   else:
+#     v2l[i] = tmp.Length[0] 
+
+# add['Make'] = add['Variant'].map(v2m)
+# add['vscore'] = add['Variant'].map(v2s)
+# add['Length'] = add['Variant'].map(v2l)
+
+def plot(param, bparam, kind='line', tight=False):
+  full.groupby(param)[bparam].mean().sort_index().plot(kind=kind)
+  plt.xlabel(param)
+  plt.ylabel(bparam)
+  if tight:
+    plt.tight_layout()
+  plt.show()
+
+model = CascadeForestRegressor(random_state=1)
+X = full[['Length', 'Beam', 'Displacement', 'Fuel', 'Water', 'Cabins', 'Draft']]
+y = full['vscore']
+model.fit(X, y)
+y_pred = model.predict(X)
+full['Predscore'] = y_pred
+mse = mean_squared_error(y, y_pred)
+print("Testing sqrt of MSE: {:.3f}, R^2: {:.3f}, MAPE: {:.2f}%".format(
+      math.sqrt(mse),
+      1 - (mse/full['vscore'].var()) * len(y_pred) / (len(y_pred) - 1),
+      full.apply(axis=1,func=lambda x:abs(x['Predscore']-x['vscore'])/x['vscore']).mean()*100
+    ))
[…]

### 2023-04-03 Program/main.py

@@ -1,13 +1,82 @@
-#!python -i
+#!/c/Users/Bardi/AppData/Local/Programs/Python/Python39/python -i
 from data_fetch import data_fetch
 from regression import regression
 import math
+import numpy as np
+import pandas as pd
 import matplotlib.pyplot as plt
 from mainstat import mainstat
+from sys import argv
 
-mst = mainstat()
+msts = {}
 
-for region in mst.regions:
-  mst.byregion(region)
+# class OutputWrapper:
+#   def __init__(self, to_file):
+#     self._to = to_file
 
-plt.show()
+#   def write(self, data):
+#     # let's write to log file with some extra string.
+#     # self._to.write("-----")
+#     self._to.write(data)
+
+def train(arg='monohulled'):
+  mst = mainstat(arg)
+  mst.initial()
+  for i in range(6):
+    mst.repeat()
+  mst.prepare()
+  mst.data_frame.to_csv(arg + '_full.csv')
+  mst.data_frame.set_index('Variant')['vscore'].to_csv(arg + '_vscore.csv')
+  # mst.data_frame['rscore'].reset_index().to_csv(arg + '_rscore.csv', index=False)
+  mst.region_pref()
+  # mst.region_preference.reset_index().to_csv(arg + '_rpref.csv', index=False)
+  msts[arg] = mst
+
+def task_train():
+  if len(argv) > 1:
+    train(argv[1])
+  else:
+    print("---monohulled")
+    train('monohulled')
+    print("---catamarans")
+    train('catamarans')
+
+def task_plot():
+  sp = msts['monohulled'].data_frame.sort_values(by='Price')['Price']
+  psp = msts['monohulled'].data_frame.sort_values(by='Price')['PredPrice']
+  plt.plot(sp[sp < 600000], psp[sp < 600000], label='Monohulled Boats')
+  sp = msts['catamarans'].data_frame.sort_values(by='Price')['Price']
+  psp = msts['catamarans'].data_frame.sort_values(by='Price')['PredPrice']
+  plt.plot(sp[sp < 600000], psp[sp < 600000], label='Catamarans')
+  plt.legend()
+
+def task_test():
+  print("==testing hong kong==")
+  print('--mono--')
+  hk = pd.read_csv('hkmono.csv')
+  msts['monohulled'].hk = 243026.933
+  msts['monohulled'].test_regression(hk, 'linear')
[…]

### 2023-04-03 Program/mainstat.py

@@ -3,22 +3,50 @@ from regression import regression
 import math
 import matplotlib.pyplot as plt
 import pandas as pd
+from scipy.stats import pearsonr
+import numpy as np
+from deepforest import CascadeForestRegressor
+from sklearn.metrics import mean_squared_error
+from sklearn.linear_model import LinearRegression
 
 class mainstat:
   data_frame = pd.DataFrame([[]],dtype='int64')
+  normal_frame = pd.DataFrame([[]],dtype='int64')
+
+  model = None
   lr = None
+  size = 0
   regions = set()
+  geos = set()
+  reg2geo = dict()
+  geo2reg = dict()
   makes = set()
   variants = set()
-  coef_cept = dict()
-  def __init__(self):
-    self.data_frame = data_fetch().data
+  coef_cept = None
+  year_mean = None
+  region_score = None
+  region_preference = None
+  variant_score = None
+  X = None
+  y = None
+  hk_rscore = 0
+
+  def __init__(self, name="monohulled"):
+    self.data_frame = data_fetch(name+".csv").data
+    self.normal_frame = self.data_frame
+    self.size = len(self.data_frame.index)
     for make in self.data_frame.Make.values:
       self.makes.add(make)
     for region in self.data_frame.CRS.values:
       self.regions.add(region)
+    for geo in self.data_frame.GeoRegion.values:
+      self.geos.add(geo)
+      self.geo2reg[geo] = set()
     for index in self.data_frame.index:
-      self.variants.add("{} {}".format(self.data_frame.loc[index].Make, self.data_frame.loc[index].Variant))
+      self.data_frame.loc[index, 'Variant'] = "{} {}".format(self.data_frame.loc[index].Make, self.data_frame.loc[index].Variant)
+      self.variants.add(self.data_frame.loc[index].Variant)
+      self.reg2geo[self.data_frame.loc[index].CRS] = self.data_frame.loc[index].GeoRegion
+      self.geo2reg[self.data_frame.loc[index].GeoRegion].add(self.data_frame.loc[index].CRS)
 
   def byregion(self, region, features=['Length', 'Year'], plot=True, make=None):
     print("Select Region: {}".format(region))
@@ -40,7 +68,285 @@ class mainstat:
     if plot:
       ax = residal.plot(legend=residal.name)
     
[…]

### 2023-04-03 Program/regression.py

@@ -46,9 +46,11 @@ class regression:
       y_pred = pd.concat([y_pred, pd.Series(self.model.predict(X_test))])
     y_pred.index = self.y.index
     y_pred.name = "pred price"
-    pred_frame = pd.concat([y_pred.apply(lambda x : math.exp(x)), self.y.apply(lambda x : math.exp(x))], axis='columns')
+    pred_frame = pd.concat([y_pred, self.y], axis='columns')
+    # pred_frame = pd.concat([y_pred.apply(lambda x : math.exp(x)), self.y.apply(lambda x : math.exp(x))], axis='columns')
     residual = pred_frame.apply((lambda x : (x.iloc[0] - x.iloc[1]) * 100 / x.iloc[1]), axis="columns")
     residual.index = range(len(residual.index))
     # residual.plot()
-    print("Square root of Evaluated MSE:", math.sqrt(mean_squared_error(self.y.apply(lambda x : math.exp(x)), y_pred.apply(lambda x : math.exp(x)))))
+    # print("Square root of Evaluated MSE:", math.sqrt(mean_squared_error(self.y.apply(lambda x : math.exp(x)), y_pred.apply(lambda x : math.exp(x)))))
+    print("Square root of Evaluated MSE:", math.sqrt(mean_squared_error(self.y, y_pred)))
     return residual

### 2023-04-03 Paper/PAPER.tex
paper

@@
 \begin{abstract}
-    Sailboats fulfill diverse roles, fueling a thriving secondary market. 
+    Sailboats fulfill diverse roles, fueling a thriving second-hand market. 
     Brokers, facing numerous complex factors, struggle to determine reasonable pricing. 
-    A tool to assist in comprehensive evaluations and rational pricing for used boats is urgently needed.
+    A tool is urgently needed to assist in comprehensive evaluations and rational pricing for used boats.
 
     This paper aims to construct a reliable model based on existing datasets, 
-    which can provide a reasonable explanation for the pricing of the second-hand sailboat market. 
+    which can provide a reasonable explanation for the pricing of the used sailboat market. 
     It also analyzes the impact of different factors and indicators on prices. 
-    Finally, the model will be applied to the second-hand sailboat market in Hong Kong to provide a reasonable and accurate pricing rule.
+    Finally, the model will be applied to the used sailboat market in Hong Kong to provide a reasonable and accurate pricing rule.
 
@@
 
-    At the very last, we analyze the strengths and weaknesses of our model as well as its
-sensitivity, whose results show that our model has high robustness, precision and accuracy.
+    Finally, we conducted an analysis of the strengths and weaknesses of our model, as well as its sensitivity.
+The results demonstrate that our model exhibits high levels of robustness, precision, and accuracy.
 After that, a report is attached.
@@
 \subsection{Background}
-In our daily lives, sailboats are not only a means of transportation, but also serve as leisure and entertainment, and even for competitive sports.
-As a result, the growing demand for sailboats has given rise to a thriving boat market, which has gradually developed into a secondary market.
-In the secondary market, buyers and sellers usually trade through brokers, who play a crucial role in the transaction process.
+In our daily lives, sailboats are not only a means of transportation but also serve as leisure, entertainment, and even for competitive sports.
+As a result, the growing demand for sailboats has given rise to a thriving boat market, which has developed into a second-hand market.
+In the market, buyers and sellers usually trade through brokers, who play a crucial role in the transaction process.
 
-For brokers, it is essential to be familiar with the used sailboat market, comprehensively consider various factors, and make reasonable pricing for the used sailboats in order to facilitate a successful transaction.
+For brokers, it is essential to be familiar with the second-hand sailboat market, comprehensively consider various factors, and make reasonable pricing for the used sailboats in order to facilitate a successful transaction.
 However, the factors affecting the price of used sailboats are numerous and complex, with different brands, variants of boats, years, depreciation rates, as well as local consumption levels and geographical environments having significant impacts.
@@
 
-Therefore, brokers urgently need a tool to assist them in making more reasonable and comprehensive evaluations of used sailboats, and to make the pricing in the used sailboat market more rational.
+Therefore, brokers urgently need a tool to assist them in making more reasonable and comprehensive evaluations of used sailboats and to make the pricing in the used sailboat market more rational.
 %问题重述
@@
 \begin{itemize}
-    \item Determine whether region has an impact on the price of second-hand boats and explain the effect.
+    \item Determine whether Region has an impact on the price of second-hand boats and explain the effect.
     \item Discuss whether any regional effect is consistent across all sailboat variants.
@@
     \item Based on the model, find out how it can be useful in the Hong Kong market.
-    \item Choose one subset and model the regional effect of Hong Kong on each sailboat prices.
+    \item Choose one subset and model the regional effect of Hong Kong on each sailboat's prices.
     \item Assess whether the effect is the same for both catamarans and monohull sailboats.
@@
 \begin{itemize}
-    \item Create a one-to two-page report with well-chosen graphics to assist the Hong Kong sailboat broker to understand your findings.
+    \item Create a one-to-two-page report with well-chosen graphics to help the Hong Kong sailboat broker to understand your findings.
 \end{itemize}
@@
 
-Next, we trained a \textbf{Heuristic Hierarchical Multiple Regression Model} to establish the relationship between year, region, variant, and price, and to abstract the effect of regions and variants on sailboat prices.
+Then, we utilized a \textbf{Hierarchical Multiple Regression} to abstractly express the Region Effect and Variant Effect, to achieve the continuous representation of the two discrete variables, Region and Variant.
+Next, we applied \textbf{Linear Regression} to obtain the relationship between Year, Region Effect, Variant Effect, and Price.
 This approach helped us capture the interactions between these variables and their influence on the pricing.
 
-Following this, we employed a \textbf{Deep Forest Model} to train the relationship between region and variant factors and their respective effects.
+Following this, we employed a \textbf{Deep Forest Model} to estimate the relationship between region and variant indicators and their respective effects.
 This advanced ensemble learning technique allowed us to predict the effect of unknown regions and variants, which in turn enabled us to further predict their prices.
@@
 As a result, we successfully developed a comprehensive and robust model (Figure \ref{fig:OurWork}) that is well-suited for Hong Kong brokers when pricing used sailboats.
-By leveraging the strengths of both Heuristic Hierarchical Multiple Regression and Deep Forest Models, our approach offers a reliable and accurate way to estimate the value of sailboats based on factors such as year, region, and variant.
+By leveraging the strengths of both Heuristic Hierarchical Multiple Regression and Deep Forest Models, our approach offers a reliable and accurate way to estimate the value of sailboats based on indicators in the dataset.
 This model serves as a valuable tool for brokers and other stakeholders in the sailboat market, facilitating informed decision-making and ensuring fair pricing practices.
@@
 	\toprule
-	\multicolumn{1}{m{3cm}}{\centering Symbol}
-	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
+
+	Symbol& Definition\\
 	\midrule
 	$l$ &Measurement data\\
+    \hline
 	$L$ &Feature vector\\
+    \hline
 	$F$ &The dimension of $L$\\
+    \hline
     $k$ &Search range\\
+    \hline
     $\lambda$ & The feature values of natural neighbors\\
+    \hline
     $nb_k(l)$ & The number of reverse neighbors of $l$ in the $k$-th iteration\\
+    \hline
     $R$ & Correlation coefficient\\
+    \hline
     $\hat{y}$ & The estimated value of $y$\\
+    \hline
     $\hat{\beta}$ & The estimated value of the regression coefficients\\
-    $\textbf{X}, \textbf{Y}$ & The variables for which the correlation is to be tested \\
-    $\textbf{P}$ & Measured value \\
-    $\textbf{Q}$ & Simulated value \\ 
+    \hline
+    $X, Y$ & The variables for which the correlation is to be tested \\
+    \hline
+    $P$ & Measured value \\
+    \hline
+    $Q$ & Simulated value \\ 
 	\bottomrule
@@
 \subsection{Data Cleaning}
-First of all, we turn the \textbf{\texttt{xlsx}} format data sheet into \textbf{\texttt{csv}} format. 
+First of all, we turn the given \textbf{\texttt{xlsx}} format data sheet into \textbf{\texttt{csv}} format. 
 The conversion causes some minor errors like extra spaces and unexcepted characters which can be easily filtered out by text editor and python string operating functions like \textbf{\texttt{strip()}} or so.
@@
 Applying $NN_k$ and $RNN(l)$ iteratively to obtain clustering centers, unclassified text samples are assigned to the nearest clustering center, and $\lambda$ is calculated as follows:
-$$\lambda=min\{k|\sum_{i=1}^{n}f(nb_k(l_i))=0\quad or\quad \sum_{i=0}^{n}f(nb_k(l_i))=\sum_{i=0}^{n}f(nb_{k-1}(l_i))\}$$
+$$\lambda=\min\{k|\sum_{i=1}^{n}f(nb_k(l_i))=0\quad or\quad \sum_{i=0}^{n}f(nb_k(l_i))=\sum_{i=0}^{n}f(nb_{k-1}(l_i))\}$$
 
@@
 
-Further more, we merge \textbf{Make} and \textbf{Variant} into a single feature, which we refer to as \textbf{Variant}.
+Further more, we merge \textbf{Make} into \textbf{Variant} into a single feature, which we refer to as \textbf{Variant}.
 
@@
 which allowed us to efficiently extract valuable information from various online sources. 
-Simultaneously, we gathered the 2020 per capita GDP data of the relevant regions to provide important economic context that might influence sailboat prices.
+Simultaneously, we gathered the 2020 GDP per capita  data of the relevant regions to provide important economic context that might influence sailboat prices.
 
@@
 
-These data collection, organization, and preprocessing efforts significantly enriched the diversity of the data and expanded the dataset size.
+These data collection, organization, and preprocessing efforts significantly enriched the diversity of the data and expanded the dataset dimension.
 By incorporating a wider range of sailboat features and relevant economic data, we were able to develop a more comprehensive understanding of the factors influencing sailboat prices. 
@@
 
-In conclusion, the meticulous data collection, organization, and preprocessing steps we undertook played a crucial role in the success of our modeling efforts. 
-By addressing issues such as duplicates and missing values, and incorporating a diverse range of ship attributes and economic data,
-we ensured the robustness and reliability of our dataset, paving the way for the development of highly effective predictive models.
-
 \subsection{Data Analysis}
-There is an abundance of labels related to sailboat specifications, which makes it challenging to discuss their individual influence on listing prices.
+There is a lot of labels related to sailboat specifications, which is complicated and may have mutually subtle relationship.
+Therefore, it is challenging to discuss their individual influence on listing prices.
 Attempting to directly perform regression on these labels using machine learning models can lead to \textbf{overfitting issues}, where the model becomes too specialized in fitting the training data and loses its ability to generalize well to new, unseen data.
@@
 To get the coefficient matrix, we typically use the least squares method to solve it:
-$$minf(x)=\sum_{i=1}^{n}L^2_i(x)=\sum_{i=1}^{n}L_i^2[y_i,f(x_i,w_i)]=\sum_{i=1}^{n}[y_i-f(x_i,w_i)]^2$$
+$$\min f(x)=\sum_{i=1}^{n}L^2_i(x)=\sum_{i=1}^{n}L_i^2[y_i,f(x_i,w_i)]=\sum_{i=1}^{n}[y_i-f(x_i,w_i)]^2$$
 
@@
 \end{figure}
-A key aspect of Model 1's success is the heuristic approach employed during each normalization step.
+A key aspect of \emph{Model 1}'s success is the heuristic approach employed during each normalization step.
 This method adapts to the size of the dataset, offering a more efficient and effective means of processing the data.
@@
     \centering
-    \includegraphics[width=.8\textwidth]{Hierarchical.png}
+    \includegraphics[width=.6\textwidth]{Hierarchical.png}
     \caption{Hierarchical Multiple Regression}\label{fig:Hierarchical}
@@
 This adaptive heuristic approach has a significant impact on the accuracy of the model's predictions, as it tailors the normalization process to suit the specific characteristics of the dataset.
-By adjusting the method used based on dataset size, Model 1 is better able to understand the underlying patterns and relationships, leading to more accurate and reliable predictions.
-
-Furthermore, the hierarchical structure of the model enables it to isolate the effects of individual variables, providing valuable insights into their specific contributions to the overall prediction.
-This granular understanding of the relationships between variables can be instrumental in guiding further analysis and informing decision-making processes.
-
-In summary, Model 1 offers a powerful and adaptive approach to price prediction, harnessing the power of heuristic hierarchical multiple regression to deliver accurate and reliable results.
-By tailoring the normalization process to suit the characteristics of the dataset and iteratively refining the model's understanding of variable relationships, Model 1 provides a robust and versatile tool for predicting prices based on input variables such as Year, Region, and Variant.
+By adjusting the method used based on dataset size, \emph{Model 1} is better able to understand the underlying patterns and relationships, leading to more accurate and reliable predictions.
 
 \subsubsection{Model 2 \textemdash  Deep Forest Model}
-However, \emph{Model 1} is somehow incomplete because \emph{Model 1} requires that the variant and region of the predicted data have appeared in the dataset before. 
-However, in actual prediction, the variant and region may be opaque to the model. 
-Taking the third question as an example, \emph{Model 1} can't predict the price of Hong Kong because the region effect of Hong Kong hasn't been evaluated by the model. 
-Therefore, we use the \textbf{Deep Forest Model} to establish \emph{Model 2}.
+
+However, the regression prediction based on \emph{Model 1} is incomplete, as \emph{Model 1} requires the variant and region of the data being predicted to have appeared in the dataset before.
+In practice, the variant and region might be unseen by the Model.
+For instance, in the third question, \emph{Model 1} cannot predict the prices in Hong Kong since the Model has not assessed the region effect for Hong Kong.
+Therefore, we employed the Deep Forest algorithm to establish \emph{Model 2}.
 
@@
 
-Deep forest is an ensemble learning model derived from the random forest approach.
-Ensemble learning techniques combine the predictions of multiple models to improve overall performance and reduce the risk of overfitting.
-In this case, the deep forest algorithm aggregates the results of numerous decision tree classifiers to produce a more accurate and stable prediction.
+Decision trees are a common machine learning method, with both classification and regression models.
+Initially, we used a basic decision tree for regression, but the model had a large error and poor accuracy for predicting prices.
+As a result, we optimized the model using the Deep Forest algorithm.
+Deep Forest is an ensemble learning model based on random forests.
+Unlike traditional decision trees, Deep Forest uses randomized strategies to train each tree-based classifier, increasing the model's diversity.
+Compared to a single decision tree, the Deep Forest model is more robust.
+The simplified process is as follows:
 
-Unlike traditional decision trees, where each tree classifier is trained using the same dataset and strategy, deep forest introduces an element of randomness to increase the diversity of the model.
-By incorporating a randomized strategy for each tree classifier, the algorithm can capture a broader range of patterns and relationships within the data.
-This stochastic approach helps to minimize the correlation between individual trees, thereby improving the model's overall performance.
-
-The deep forest model has several advantages over a single decision tree.
-First, it is more robust, as it leverages the wisdom of multiple tree classifiers to arrive at a consensus prediction.
-This aggregation process helps to reduce the impact of any single tree's errors, ensuring that the overall prediction is more reliable.
-Second, the deep forest model is less susceptible to overfitting, a common issue in machine learning where a model learns the training data too well and performs poorly on new, unseen data.
-By using a randomized strategy to train each tree classifier, deep forest reduces the likelihood of overfitting and improves the model's generalization capabilities.
 \begin{figure}[htbp]
     \centering
-    \includegraphics[width=1\textwidth]{Deep_forest2.png}
+    \includegraphics[width=.8\textwidth]{Deep_forest2.png}
     \caption{Deep Forest Model}\label{fig:DF2}
 \end{figure}
-Another key benefit of the deep forest model is its ability to handle both categorical and continuous features, making it highly versatile for various types of problems.
-Additionally, the deep forest algorithm's structure enables it to be easily parallelized, allowing for efficient processing on multi-core processors or distributed computing environments.
 
-In summary, the deep forest algorithm is an effective and robust machine learning method that addresses the limitations of traditional decision trees.
-By employing an ensemble learning approach and incorporating randomized strategies for training tree classifiers, deep forest models can deliver more accurate and reliable predictions.
-These features make the deep forest model particularly well-suited for challenging tasks, such as predicting prices, where a high degree of accuracy and stability is essential for success.
+First, we expanded the dataset to obtain quantitative data for the region and variant.
+Specifically, for the variant, we expanded data such as draft, beam, water tank, fuel tank, cabins, and displacement.
+For the region, we expanded data such as GDP per capita, Gini coefficient, and Human Development Index.
+When dealing with unmarked variants and regions, we first applied \emph{Model 1} to obtain the effect of marked variants and regions.
+Then, we applied the effect of marked variants and regions to the Deep Forest, regressing through the expanded data to obtain the effect of unmarked variants and regions, and thus predicting the price.
 
@@
 \end{figure}
-
-As for \emph{Model 2}, we first expanded the dataset to obtain quantified data for regions and variants.
-Specifically, for variants, we expanded data such as \texttt{draft}, \texttt{beam}, \texttt{water tank}, \texttt{fuel tank}, \texttt{cabins}, \texttt{displacement}, etc. 
-For regions, we expanded data such as \texttt{GDP}, \texttt{Gini coefficient}, \texttt{Human Development Index}, etc. 
-When dealing with unmarked variants and regions, we first used \emph{Model 1} to obtain the effects of marked variants and regions, and then applied the effects of marked variants and regions to the deep forest.
-By expanding the data for regression, we obtained the effects of unmarked variants and regions, and thus predicted the price.
 
@@
 For accuracy analysis, we use the correlation coefficient $R$ and Mean Absolute Percentage Error (MAPE) as evaluation metrics.
-$$R(\textbf{X},\textbf{Y})=\frac{\text{cov}(\textbf{X},\textbf{Y})}{\sqrt{\text{var}[\textbf{X}] \text{v         ar}[\textbf{Y}]}}$$
+$$R(\textbf{X},\textbf{Y})=\frac{\text{cov}(\textbf{X},\textbf{Y})}{\sqrt{\text{var}[\textbf{X}] \text{var}[\textbf{Y}]}}$$
 $$\text{MAPE} = \frac{\sum_{i = 1}^n (\frac{|\textbf{P} - \textbf{Q}|}{\textbf{P}} \times 100\%)}{n}$$
@@
     $$\text{cov}(\textbf{X},\textbf{Y})=\frac{\sum_{i=1}^{n}(\textbf{X}_i-\overline{\textbf{X}})(\textbf{Y}_i-\overline{\textbf{Y}})}{n-1}$$
+
+    \begin{table}[htbp]
+        \centering
+        \begin{tabular}{c|c|c}
+        Train& Cata& Mono \\
+        \hline
+        \hline
+        $R^2$ & 0.924 & 0.974 \\
+        \hline
+        MAPE & 5.09\% & 7.29\% \\
+        \hline
+        \end{tabular}
+        \qquad
+        \begin{tabular}{c|c|c}
+        Test& Cata& Mono \\
+        \hline
+        \hline
+        $R^2$ & 0.901 & 0.942 \\
+        \hline
+        MAPE & 10.16\% & 11.65\% \\
+        \hline
+        \end{tabular}
+        \qquad
+        \begin{tabular}{c|c|c}
+        HK& Cata& Mono \\
+            \hline
+            \hline
+            $R^2$ & 0.849 & 0.885 \\
+            \hline
+            MAPE & 7.18\% & 8.70\% \\
+            \hline
+            \end{tabular}
+        \caption{Accuracy of Train Set, Test Set and HK Set}
+        \label{tab:Accuracy}
+    \end{table}
+
 \section{Regional Effect Analysis}
@@
 
-\section{The applicability of The Prediction Model in Hong Kong}
+\section{The Applicability of The Prediction Model in Hong Kong}
 When applying our model to the Hong Kong region, 
-we first assume that we can obtain the Year, Variant, and Region parameters for the used sailboats. 
-For the given geographic regions, we start by using \emph{Model 2} to determine the Region Effect, leveraging the area's GDP data.
+we first try to obtain the indicators for the used sailboats. 
+For Hong Kong, we start by using \emph{Model 2} to determine the Region Effect, leveraging the area's GDP per capita data.
 
@@
 
-\section{Further Improvements}
-
 \section{Strengths and Weaknesses}
@@
 
-\textbf{Comprehensiveness:}
-After the basic data processing, we significantly expanded the dataset, including extending the Variant to Draft, Beam, Displacement, Water tank, Fuel tank, and Cabin, as well as expanding the Region to GDP, HDI, and Gini coefficient.
+\textbf{Strength-1 Comprehensiveness:}
+After the basic data processing, we significantly expanded the dataset, including extending the Variant to Draft, Beam, Displacement, Water tank, Fuel tank, and Cabin, as well as expanding the Region to GDP per capita.
 We performed correlation tests for each variable, making the modeling process extensive and comprehensive.
 
-\textbf{Innovative:}
+\textbf{Strength-2 Innovative:}
 Our model combines heuristic learning and hierarchical multivariate regression, obtaining accurate predictions through continuous iteration.
@@
 
-\textbf{Accuracy:}
+\textbf{Strength-3 Accuracy:}
 Our model performs exceptionally well in terms of both error analysis and accuracy, achieving 94.91\% on the Catamarans test set and 92.71\% on the Monohulled Boats test set.
@@
 
-\textbf{Applicability:}
+\textbf{Strength-4 Applicability:}
 When applied to the Hong Kong market, the model maintains a high level of accuracy, demonstrating its excellent applicability.
@@
 \subsection{Weaknesses}
-\textbf{Time consuming:}
+\textbf{Weakness-1 Time consuming:}
 The model can achieve satisfactory regression results after 2-3 iterations when processing the data for this task.
@@
 
-\textbf{Lack of geography  factor analysis:}
+\textbf{Weakness-2 Lack of geography  factor analysis:}
 Due to the difficulty in obtaining geographical data and the challenge of analyzing and quantifying factors such as climate, the model does not include geographical factors.
 Despite this limitation, the model still provides valuable insights and accurate predictions for the used sailboat market.
+
+\section{Further Improvements}
+Although our Model has been optimized over several days, evolving from a simple decision tree to an organic combination of Heuristic Hierarchical Multiple Regression and Deep Forest, both \emph{Model 1} and \emph{Model 2} have produced excellent results in price prediction.
+However, during each iteration, we still only used a simple regression model, with accuracy being the result of iteration and heuristic learning.
+Upon reviewing the model, we identified the following two issues:
+\begin{itemize}
+    \item When fitting the Variant Effect, we lost regional information.
+    \item Combined Make and Variant, causing the model to overlook the premium issue between different Makes.
+\end{itemize}
+\subsection{Lasso Regression Update for Model}
+To address the first issue, we decided to use Lasso Regression to replace the simple linear regression in each iteration process.
+The characteristics of Lasso Regression, which can avoid the problem of multicollinearity, also resolved the shortcomings of the original model.
+In each round of iterative regression, we only need to perform Lasso Regression on Variant and Region once, avoiding the loss of regional information.
+The specific formula is as follows:
+
+$L_1,L_2$ regularization:
+$$L_1=\lambda\sum_{j=1}^{p}|\beta_j|,L_2=\sum_{j=1}^{p}\beta_j^2$$
+
+Lasso Regression's loss function:
+$$\text{minizize }\frac{1}{2n}||y-X\beta||_2^2+\lambda||\beta||_1$$
+
+Assume $\beta_i=\{\beta_{i1},\beta_{i2},\beta_{i3}\}$After introducing Lasso Regression, the model's process becomes:
+\begin{itemize}
+    \item \textbf{Step 1:} Since the relationship between year and price is highly linear, we first normalize the Year parameter to remove its influence,we can get $\beta_{11}$.
+    \item \textbf{Step 2:} Then apply Lasso Regression to simultaneously normalize Variant and Region, combining the original functions $f_1(\beta_{12})\&g(\beta_{13})$ into $h_1(\beta_{12},\beta_{13})$.
+    \item \textbf{Step 3:} Feeding $\beta_1=\{\beta_{11},\beta_{12},\beta_{13}\}$ into the iterative heuristic learning function.
+We perform iterative regression to obtain $h_1(\beta_{12},\beta_{13}),h_2(\beta_{22},\beta_{23}),\cdots,h_n(\beta_{n2},\beta_{n3})$ until the desired accuracy is reached, resulting in the final matrix $\beta_n=\{\beta_{n1},\beta_{n2},\beta_{n3}\}$.
+    \item \textbf{Step 4:} Using $\beta_n$ for regression prediction, we obtain the predicted value.
+\end{itemize}
+
+This process is similar to the basic model idea.
+We also tried to update the model using Lasso Regression and re-predict the price.
+However, due to the lack of precision in the design matrix and the difficulty in controlling the regularization strength, the update was unsuccessful.
+Nonetheless, based on the initial improved model results and the Lasso Regression loss function, we can predict that the improved model will address multicollinearity issues for correlated Variant and Region variables.
+
+\subsection{Better utilization of the Deep Forest}
+As previously mentioned, we used Lasso Regression to address the issue of losing regional information when fitting the Variant Effect.
+For the second issue, we considered fully utilizing Deep Forest by applying it to the regression process of \emph{Model 1}.
+Since Random Forest employs random sampling and feature selection, it can reduce the influence between correlated variables, thereby reducing multicollinearity problems, enhancing the stability and predictive accuracy of the regression model.
+Therefore, we do not need to combine Make and Variant into a single Variant variable for regression analysis.
+Instead, we can input all the screened variables into Deep Forest, allowing the model to self-prune and fit, enhancing robustness and generalization capabilities,then we get the graph below:
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{update.png}
+    \caption{Optimizing Model Performance}\label{fig:update}
+\end{figure}
+
+We tested the optimized model on the training set and obtained the following results: Clearly, Deep Forest performs better in handling noise.
+However, on the other hand, due to the small dataset and the limited number of samples for some categories, Deep Forest exhibited some overfitting and underfitting phenomena.
+Moreover, since \emph{Model 2} also employed the Random Forest algorithm, this led to nested Random Forests, resulting in significant computational overhead.
+Compared to the increase in accuracy, the exponential growth of overhead is not worth the cost.
+Therefore, simply replacing the model with Deep Forest is not a perfect solution, and the model still requires further optimization and adjustment.However, from the preliminary results, it can be seen that the use of Deep Forest in the regression part does provide a solution to the second issue.
+We firmly believe that through structural adjustments, the model's performance will undoubtedly be further optimized!
 
@@
 \begin{flushleft}  % 左对齐环境，无首行缩进
-\textbf{To:} Heishan Yan\\
-\textbf{From:} Team 1234567\\
-\textbf{Date:} October 1st, 2019\\
-\textbf{Subject:} A better choice than MS Word: \LaTeX
+\textbf{To:} The sailboat broker in Hong Kong\\
+\textbf{From:} Team \#2332102\\
+\textbf{Date:} Apr 3th, 2023\\
+\textbf{Subject:} 
+\noindent\rule[0.25\baselineskip]{\textwidth}{1pt}
 \end{flushleft}
@@
 
-% 以下为附录内容
-% 如您的论文中不需要附录，请自行删除
-\begin{subappendices}  % 附录环境
-
-\section{Appendix A: Further on \LaTeX}
-To clarify the importance of using \LaTeX\ in MCM or ICM, several points need to be covered, which are \ldots
-
-To be more specific, \ldots
-
-All in all, \ldots
-
-Anyway, nobody \textbf{really} needs such appendix \ldots
-
-\section{Appendix B: Program Codes}
-Here are the program codes we used in our research.
-
-% 代码环境示例三则
-% 如您的论文不需要展示代码，请删除
-% 更多用法，请参考 listings 宏包文档
-
-% Python 代码示例
-\begin{lstlisting}[language=Python, name={test.py}]
-# Python code example
-for i in range(10):
-    print('Hello, world!')
-\end{lstlisting}
-
-% MATLAB 代码示例
-\begin{lstlisting}[language=MATLAB, name={test.m}]
-% MATLAB code example
-for i = 1:10
-    disp("hello, world!");
-end
-\end{lstlisting}
-
-% C++ 代码示例
-\begin{lstlisting}[language=C++, name={test.cpp}]
-// C++ code example
-#include <iostream>
-using namespace std;
-
-int main() {
-    for (int i = 0; i < 10; i++)
-        cout << "hello, world" << endl;
-    return 0;
-}
-\end{lstlisting}
-
-\end{subappendices}  % 附录内容结束
-
 \end{document}  % 结束

### 2023-04-03 Paper/PAPER.tex
paper

@@
 
-    For Data Exploration, \dots
+    For Data Exploration, we first try to preprocess the data with \textbf{Adaptive Density-Based Clustering} and \textbf{Linear Interpolation} methods.
+    Moreover, we use the web strapper to fetch more data to expand the dimensions of our data.
+Simple statistical analysis shows that sub-indicators center around the \emph{year}, \emph{variant}, and \emph{region}.
 
-    For Problem(a), \dots
+    For Problem(a), We adopt a \textbf{Heuristic Multilevel Regression Model} inspired by the conclusion drawn from data analysis, and introduce the concept of \textbf{impurity} to heuristically evaluate interrelation among variables, avoid bias by introducing \textbf{feedback and renormalization}.
+    And our model achieves good precision on both the train set and the test set.
 
-    For Problem(b), \dots
+    For Problem(b), 
+    We apply \textbf{statistic analysis} of the distribution of the average price to find the regions' impacts.
+    After using \textbf{normalization techniques} and \textbf{impurity analysis}, it can be concluded that the regional effect is not significant across variants and primarily takes effect by featuring variants of different prices.
+    Practically and statistically, the GDP per capita is found of a linear correlation with the average variant prices of a region with \textbf{linear correlation coefficient} and \textbf{p-testing}.
 
-    For Problem(c), \dots
+    For Problem(c),
+    our model can be fitted into the Hong Kong market using our model's \textbf{regional sub-indicators}.
+    Besides, we spot a significant underestimation of our model when fitting it into Hong Kong's market in the subset of the catamarans' market.
+    however, this regional effect is not found in the subset of the monohulled sailboats market.
 
-    For Problem(d), \dots
+    For Problem(d), we find interesting patterns between the length and the region.
 
-    For Problem(e), \dots
-
-    Finally, we conducted an analysis of the strengths and weaknesses of our model, as well as its sensitivity.
-The results demonstrate that our model exhibits high levels of robustness, precision, and accuracy.
+    Finally, we conducted an analysis of the strengths and weaknesses of our model.
+Besides, we further \textbf{optimized the model} and the results demonstrate that our model exhibits high levels of robustness, precision, and accuracy.
 After that, a report is attached.
@@
     \vspace{5pt}
-    \textbf{Keywords}:  Linear interpolation, Adaptive Density-Based Clustering, Heuristic Hierarchical Multiple Regression, Deep Forest Model,  Machine Learning, Analysis of Variance.
+    \textbf{Keywords}: Used Sailboat Pricing, Adaptive Density-Based Clustering, Heuristic Hierarchical Multiple Regression, Feedback Model, Deep Forest Model, Analysis of Variance.
 
@@
 
-Then, we utilized a \textbf{Hierarchical Multiple Regression} to abstractly express the Region Effect and Variant Effect, to achieve the continuous representation of the two discrete variables, Region and Variant.
+Then, we utilized a \textbf{Hierarchical Multiple Regression} to abstractly express the Region's Effect and Variant's Effect, to achieve the continuous representation of the two discrete variables, Region and Variant.
 Next, we applied \textbf{Linear Regression} to obtain the relationship between Year, Region Effect, Variant Effect, and Price.
@@
 In practice, the variant and region might be unseen by the Model.
-For instance, in the third question, \emph{Model 1} cannot predict the prices in Hong Kong since the Model has not assessed the region effect for Hong Kong.
+For instance, in the third question, \emph{Model 1} cannot predict the prices in Hong Kong since the Model has not assessed the region's effect for Hong Kong.
 Therefore, we employed the Deep Forest algorithm to establish \emph{Model 2}.
@@
 
+\begin{figure}[htbp]
+        \centering
+        \includegraphics[width=.8\textwidth]{accuracy.jpg}
+        \caption{Model Fitting Accuracy}\label{fig:accuracy}
+\end{figure}
+
 \begin{table}[htbp]
@@
     \includegraphics[width=1\textwidth]{region_effect.png}
-    \caption{Region Effect}\label{fig:region_effect}
+    \caption{Region's Effect}\label{fig:region_effect}
 \end{figure}
@@
 we first try to obtain the indicators for the used sailboats. 
-For Hong Kong, we start by using \emph{Model 2} to determine the Region Effect, leveraging the area's GDP per capita data.
+For Hong Kong, we start by using \emph{Model 2} to determine the Region's Effect, leveraging the area's GDP per capita data.
 
 If the predicted Variant is present in the training set, 
-we can directly use \emph{Model 1} to estimate the pricing by incorporating the Region Effect, Variant Effect, and Year. 
-However, if the predicted Variant is not in the training set, we first need to use \emph{Model 2} to obtain the Variant Effect by considering factors such as beam, draft, and displacement. 
-Once the Variant Effect is determined, we can then employ \emph{Model 1} to make the final price prediction.
+we can directly use \emph{Model 1} to estimate the pricing by incorporating the Region's Effect, Variant's Effect, and Year. 
+However, if the predicted Variant is not in the training set, we first need to use \emph{Model 2} to obtain the Variant's Effect by considering factors such as beam, draft, and displacement. 
+Once the Variant's Effect is determined, we can then employ \emph{Model 1} to make the final price prediction.
 
@@
 
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{accuracy.jpg}
+    \caption{Model Fitting Accuracy in HongKong}\label{fig:HongKong}
+\end{figure}
+
+Interestingly, this regional effect is not observed in the subset of the monohulled sailboats market, suggesting that there are unique factors at play when it comes to the catamarans' market in Hong Kong.
+Upon further examination, we have deduced that the reason behind this discrepancy is likely due to Hong Kong's flourishing tourism industry.
+
+Catamarans are widely regarded as superior to monohulled sailboats for travelers, offering a more stable and comfortable platform for sightseeing, relaxation, and entertainment.
+With the increasing number of tourists visiting Hong Kong, it is no surprise that the demand for catamarans has surged, thus contributing to the underestimation of our model's effectiveness in this particular market segment.
+
+In conclusion, while our model has shown promising results in various aspects of the Hong Kong market, it is essential to recognize the unique regional factors that may affect its performance in certain subsets.
+By refining our model to account for these factors, we can ensure a more accurate and robust representation of the market dynamics at play.
+In doing so, our model will be better equipped to guide businesses and investors in making informed decisions, ultimately leading to a more prosperous and thriving economy in Hong Kong.
+
 \section{Extended Inferences or Conclusion}
+Upon conducting a thorough analysis of the relationship between various variables, excluding the average price and region, using linear correlation analysis tools, we have uncovered some intriguing patterns between the boat length and the region.
+
+The analysis results reveal that people in European regions tend to prefer sailing longer boats, while individuals in the Caribbean area are fond of navigating more extended catamarans.
 
@@
 \begin{itemize}
-    \item When fitting the Variant Effect, we lost regional information.
+    \item When fitting the Variant's Effect, we lost regional information.
     \item Combined Make and Variant, causing the model to overlook the premium issue between different Makes.
@@
 \subsection{Better utilization of the Deep Forest}
-As previously mentioned, we used Lasso Regression to address the issue of losing regional information when fitting the Variant Effect.
+As previously mentioned, we used Lasso Regression to address the issue of losing regional information when fitting the Variant's Effect.
 For the second issue, we considered fully utilizing Deep Forest by applying it to the regression process of \emph{Model 1}.
@@
     \centering
-    \includegraphics[width=.8\textwidth]{update.png}
+    \includegraphics[width=.7\textwidth]{update.png}
     \caption{Optimizing Model Performance}\label{fig:update}
@@
 
-In the memo, we want to introduce you an alternate typesetting program to the prevailing MS Word: \textbf{\LaTeX}.
-In fact, the history of \LaTeX\ is even longer than that of MS Word.
-In 1970s, the famous computer scientist Donald Knuth first came out with a typesetting program, which named \TeX\ \ldots
+\noindent \textbf{\emph{Part One - Model Accuracy}}
 
-Firstly, \ldots
+The two line charts presented above use the actual prices as the x-axis and the predicted values from our model as the y-axis.
+The fit between the line and the $y=x$ equation demonstrates the accuracy of our model.
+Clearly, our model is highly effective in predicting the prices of used boats worldwide.
+We have tested the model's accuracy, achieving 94.91\% for Catamarans and 92.61\% for Monohulled Sailboats.
+Thus, our model is fundamentally accurate in its price predictions.
 
-Secondly, \ldots
+\noindent \textbf{\emph{Part Two - Analysis of Variance}}
 
-Lastly, \ldots
+Figure 3 reveals a strong linear correlation between price and year.
+The model shows that the Region's Effect influences market prices by affecting boat types.
+In particular, areas with higher per capita GDP tend to buy more expensive boat types, leading to higher average prices for used boats in these regions.
 
-According to all those mentioned above, it is really worth to have a try on \LaTeX!
+\noindent \textbf{\emph{Part Three - Model of Hong Kong}}
+
+Comparing the slopes of the two regression models in Figure 4, we see that regional economic conditions impact both boat types.
+However, in Hong Kong, we found that the extra-regional effect is not found in the subset of the monohulled sailboats market.
+We infer that this is probably because of Hong Kong's prosperous tourism -- catamarans are better than monohulled sailboats for travelers.
+
+\noindent \textbf{\emph{Part Four - Interesting Conclusion}}
+
+Based on the two bar charts, we have drawn an interesting conclusion: the analysis results reveal that people in European regions tend to prefer sailing longer boats, while individuals in the Caribbean area are fond of navigating more extended catamarans.
+This phenomenon may be related to local geography and culture.
 
@@
 \end{letter}
+
 \clearpage

### 2023-04-03 Paper/PAPER.tex
paper

@@
 \newcommand{\upcite}[1]{\textsuperscript{\textsuperscript{\cite{#1}}}} 
-\title{Title}  % 标题
+\title{Pricing Used Sailboats : A Combination Model Based on Heuristic Multilevel Regression and Deep Forest}  % 标题
 
@@
 
-    For Problem(a), We adopt a \textbf{Heuristic Multilevel Regression Model} inspired by the conclusion drawn from data analysis, and introduce the concept of \textbf{impurity} to heuristically evaluate interrelation among variables, avoid bias by introducing \textbf{feedback and renormalization}.
+    For Problem(a), Inspired by the previous conclusion, we adopt a \textbf{Heuristic Multilevel Regression Model} for making the three \emph{discrete} variables \emph{continuous}, introduce the concept of \textbf{impurity} to heuristically evaluate interrelation among variables, and avoid bias by introducing \textbf{feedback and renormalization}.
+Finally, we use \textbf{Deep Forest} to regress them to the price.
     And our model achieves good precision on both the train set and the test set.
@@
     \hline
-    $X, Y$ & The variables for which the correlation is to be tested \\
-    \hline
     $P$ & Measured value \\
@@
     $Q$ & Simulated value \\ 
+    \hline
+    $\alpha$ & p-value significance level \\
+    \hline
+    $df$ & freedom \\
+    \hline
+    $s$ & standard deviation \\
+    \hline 
+    $T$ & t-distribution \\
+
 	\bottomrule
@@
 \end{table}
+
 \section{Data Exploration}
@@
 \subsubsection{Model 1 \textemdash  Heuristic Hierarchical Multiple Regression}
+Inspired by the conclusion drawn from data analysis, we adopt a multilevel heuristic model that utilizes the purity of the samples grouped by specific variables.
+We introduce impurity to model a variable's independence from other variables.
 
-\emph{Model 1}, as illustrated in Figure \ref{fig:Model1}, is specifically designed to predict prices by taking into account input variables such as Year, Region, and Variant.
+To be specific, we begin with the year variable mentioned above.
+
+The impurity by a variable can be measured by the weighted mean variance of all groups divided by the variable.
+
+Unavoidably, the initial impurity will damage our model's accuracy.
+For example, we have supposed that the year variable is independent of other variables for the first round of normalization (otherwise we cannot resolve the problem at the beginning), making our normalizing coefficient of this variable biased.
+
+Therefore, we introduce the feedback model into our model.
+To be exact,   after the first round has been completed, compared to the initial state, we have more information about the year, variant, and region factors' effect.
+Therefore, we repeatedly renormalize the factors to gain a more accurate coefficient (factors' effect).
+
+Specifically, \emph{Model 1}, as illustrated in Figure \ref{fig:Model1}, is specifically designed to predict prices by taking into account input variables such as Year, Region, and Variant.
 To achieve accurate predictions, this model incorporates a heuristic hierarchical multiple regression approach, which distinguishes it from conventional regression methods.
@@
         \centering
-        \includegraphics[width=.8\textwidth]{accuracy.jpg}
-        \caption{Model Fitting Accuracy}\label{fig:accuracy}
+        \begin{subfigure}[b]{.4\textwidth}
+        \includegraphics[width=\textwidth]{accuracy1.jpg}
+        \caption{The fitting performance before denoising.}\label{subfig:accuracy1}
+        \end{subfigure}
+        \begin{subfigure}[b]{.4\textwidth}
+        \includegraphics[width=\textwidth]{accuracy2.png}
+        \caption{The fitting performance after denoising.}\label{subfig:accuracy2}
+        \end{subfigure}
+        \caption{Model Fitting Accuracy in HongKong}\label{fig:accuracy}
     \end{figure}
@@
 \section{Regional Effect Analysis}
+
 Applying \emph{Model 1}, we can easily abstract the effect of each region. 
 Therefore, by normalizing the year and variant, 
-we can clearly see the effect of each region(see Figure \ref{fig:region_effect}).
+we can clearly see the effect of each region(see Figure \ref{fig:region_effect1}).
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{region_effect.png}
-    \caption{Region's Effect}\label{fig:region_effect}
+    \includegraphics[width=1\textwidth]{region_effect1.png}
+    \caption{Region's Effect}\label{fig:region_effect1}
 \end{figure}
+
+After normalizing the year and the variant factor (thus eliminating their influence), we surprisingly find that the distribution of average price among regions turns much more uniform than that of the initial state.
+Moreover, the imparity by variants is small as soon as the year factor is normalized(see Figure \ref{fig:region_effect2}).
+So we can conclude that the regional effect is not significant across variants.
+And it's necessary to note that the regional effect mainly takes effect by featuring variants of different prices.
+
+Practically, the economic development level of the region best describes the region effect we found.
+Statistically, the GDP per capita is found of a strong positive linear correlation with the average variant prices of a region with linear correlation coefficient and p-testing.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.9\textwidth]{region_effect2.png}
+    \caption{Region's Effect after nomarlizing Variant}\label{fig:region_effect2}
+\end{figure}
+
+To verify the significance of linear correlation, we should perform p-testing:
+Assuming that we choose $\alpha$ as the significance level for the p-value test (usually 0.01, 0.05, or 0.10) and the hypothesis is denoted as $H_0$, we first calculate the means and standard deviations of the two samples, denoted as $\bar{x}$ and $s$.
+Then, we calculate the t-value using the following formula:
+$$t=\frac{\bar{x}_1-\bar{x}_2}{\sqrt{\frac{s_1^2}{n_1}+\frac{s_2^2}{n_2}}}$$
+
+We calculate the degrees of freedom as $df = n_1 + n_2 - 2$, and then use the degrees of freedom and the significance level to look up the critical value of t from the t-distribution table with n-1 degrees of freedom.
+From this, we obtain the p-value:
+$$p=2\times P(T>|t|)$$
+
+Because we need to make a judgment about the correctness of the hypothesis $H_0$, we need to perform the following evaluation:
+$$\begin{cases}
+    p \geq\alpha ,\quad cannot \quad reject\quad H_0\\p<\alpha,\quad can \quad reject\quad H_0
+    \end{cases}$$
 
@@
     \centering
-    \includegraphics[width=.8\textwidth]{accuracy.jpg}
-    \caption{Model Fitting Accuracy in HongKong}\label{fig:HongKong}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{HK1.png}
+    \caption{Monohulled Sailboats}\label{subfig:HK1}
+    \end{subfigure}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{HK2.png}
+    \caption{Catamaran}\label{subfig:HK2}
+    \end{subfigure}
+    \caption{Model Fitting Accuracy in HongKong}\label{fig:HK}
 \end{figure}
@@
 Moreover, the model can improve its accuracy through self-iteration and possesses heuristic learning capabilities.
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{strength1.png}
+    \caption{Single Cycle}\label{subfig:SG1}
+    \end{subfigure}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{strength2.png}
+    \caption{Muticycle}\label{subfig:SG2}
+    \end{subfigure}
+    \caption{Model accuracy improvement}\label{fig:strength}
+\end{figure}
 
@@
 
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{report1.png}
+    \caption{Monohulled Sailboats}\label{subfig:report1}
+    \end{subfigure}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{report2.png}
+    \caption{Catamaran}\label{subfig:report2}
+    \end{subfigure}
+    \caption{Model Fitting Accuracy}\label{fig:Report1}
+\end{figure}
+
 The two line charts presented above use the actual prices as the x-axis and the predicted values from our model as the y-axis.
@@
 
-Figure 3 reveals a strong linear correlation between price and year.
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{monohulled_price_year.png}
+    \caption{Monohulled Sailboats}\label{subfig:report3}
+    \end{subfigure}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{catamaran_price_year.png}
+    \caption{Catamaran}\label{subfig:report4}
+    \end{subfigure}
+    \caption{The relationship between year and price}\label{fig:Report2}
+\end{figure}
+
+Figure 15 reveals a strong linear correlation between price and year.
 The model shows that the Region's Effect influences market prices by affecting boat types.
 In particular, areas with higher per capita GDP tend to buy more expensive boat types, leading to higher average prices for used boats in these regions.
+\clearpage
+\noindent \textbf{\emph{Part Three - Model of Hong Kong}}
 
-\noindent \textbf{\emph{Part Three - Model of Hong Kong}}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=.5\textwidth]{report5.jpg}
+    \caption{Optimizing Model Performance}\label{fig:Report3}
+\end{figure}
 
@@
 \noindent \textbf{\emph{Part Four - Interesting Conclusion}}
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{.45\textwidth}
+    \includegraphics[width=\textwidth]{report3.png}
+    \caption{Monohulled Sailboats}\label{subfig:report5}
+    \end{subfigure}
+    \begin{subfigure}[b]{.4\textwidth}
+    \includegraphics[width=\textwidth]{report4.png}
+    \caption{Catamaran}\label{subfig:report6}
+    \end{subfigure}
+    \caption{Preferences for boat lengths vary among different regions}\label{fig:Report4}
+\end{figure}
 
